---
title: "Rasterize VRI"
author: "dwaddell"
date: '2022-05-09'
output: md_document
---


Using only R-4.1.3 
Package: sf  

No GDAL or Python installed.  

Workstation config: 32GB RAM  


Rasterize VRI from GDB  
Previously impossible on 32 GB machine using R.  

sf::gdal_utils relies on backed C++ gdal rasterize function.  
This relieves the memory load from R.  

Add the gr_skey as a sequence key. 


## Rasterize GDB  

Reads: VEG_COMP_LYR_R1_POLY_2020.gdb  
Produces: vri_2021_init.tif  

Not initially masked for Water and Land  



Produces: vri_2021_init.tif  
Naming follows the FAIB AR standard for year. 

Note that the supplied file is extracted from:
https://catalogue.data.gov.bc.ca/dataset/vri-2020-forest-vegetation-composite-layer-1-l1-  


Publication date: 2021-02-08  


Start: `r Sys.time()`

```{r rasterize_gdb}

library(sf)
library(terra)

drive <- substr(getwd(),1,1)

# read gdb file

src <- paste0(drive,':/data/data_projects/vri_gdb/VEG_COMP_LYR_R1_POLY_2020.gdb')
dest <- paste0(drive,':/data/data_projects/vri_gdb/vri_2021_init.tif')


gdal_utils("rasterize",src,dest,options = 
             c('-tr','100',' 100',
                '-te','159587.5 ','173787.5 ','1881187.5 ','1748187.5',
                '-ot', 'UInt32 ',
                '-l', 'VEG_COMP_LYR_R1_POLY',
                '-a', 'FEATURE_ID' ,
                '-a_srs','EPSG:3005',
                '-a_nodata', '-99',
                '-co','COMPRESS=LZW'),
                '-overwrite')


```

End GDB -> Tif: `r Sys.time()`

## Mask for Water

Produces: vri_2021_fid.tif  

Note: mask was supplied by Mike Fowler (FAIB)

```{r apply_mask}

# read the tif
f3 <- paste0(substr(getwd(),1,1),':/data/data_projects/vri_gdb/vri_2021_init.tif')
base_raster <- rast(f3)

# force the CRS 
crs(base_raster) <- 'epsg:3005'

# land / water mask supplied by Mike F.
f4 <- paste0(substr(getwd(),1,1),':/data/data_projects/base_maps/land_water.tif')
mask_raster <- rast(f4)

# this mask is a 0/1 of land water
# there are values of 0 between Vancouver Island and the mainland.
# these need to be set to NA to be used as a land mask
# set values in mask to NA where 0
mask_raster[mask_raster==0] <- NA

# force the CRS
crs(mask_raster ) <- 'epsg:3005'


# set no data to 0 in the base tif
# this will include water and any isolated nodata values inside land
base_raster[is.na(base_raster)] <- 0

# apply the land mask
# filter out the water
base_raster_masked <- mask(base_raster,mask_raster)

# filter out any zeros
# set to NA
base_raster_masked[base_raster_masked==0] <- NA

# write to final tif

fName <- paste0(substr(getwd(),1,1),':/data/data_projects/vri_gdb/vri_2021_fid.tif')
writeRaster(base_raster_masked, fName, datatype='INT4U',overwrite=TRUE)



```


## Raster Brick

Add a sequence key to the original data.  

Produces: vri_2021_fid_gr_skey.tif  

Create a 2 band GeoTiff with:  

- feature_id
- gr_skey

```{r create_brick}

# set up for gr_skey
row <- 15744
col <- 17216
max_no <- row * col

# create a second raster
base_copy <- base_raster_masked

# set values to sequence
base_copy[] <- 1:max_no

# apply the mask
base_copy <- mask(base_copy,mask_raster)

# check that there are no zeros
# take a copy
r3 <- base_copy

# where values are greater than 0 set to 1
r3[r3 >0] <- 1

# check the frequency
# should all be 1's
freq(r3)

# reset the layer names
names(base_raster_masked) <- 'feature_id'
names(base_copy) <- 'gr_skey'

# create list of rasters
lst <- list(base_raster_masked,base_copy)

# create a stack of these rasters from list
raster_stack <-rast(lst)

# write this to a tiff
fName <- paste0(substr(getwd(),1,1),':/data/data_projects/vri_gdb/vri_2021_fid_gr_skey.tif')
writeRaster(raster_stack, fName, datatype='INT4U', overwrite=TRUE)


```


End: `r Sys.time()`
