---
title: "PSPL FTP Extract"
author: "D. Waddell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: md_document

---

## Load compressed PSPL gdb files to processing location

## directory locations are fixed as follows:

PSPL GDB Files        :/Data/Data_projects/AR2022/PSPL/gdb_data

And is copied from:  

\\tension.dmz\ftp\HTS\external\!publish\Provincial_Site_Productivity_Layer\Site_Prod_with_Approved_PEM_TEM\Site_Prod_Point_FGDBs



Load Date: `r Sys.Date()`
Start:  `r format(Sys.time(),"%c")`



Copy PSPL data from FTP site  

```{r copy_pspl_data, eval = TRUE, echo=FALSE, message=FALSE,warning=FALSE}

# this is the FTP folder
ftp_pspl_folder <- '\\\\tension.dmz\\ftp\\HTS\\external\\!publish\\Provincial_Site_Productivity_Layer\\Site_Prod_with_Approved_PEM_TEM\\Site_Prod_Point_FGDBs'

# this is where the zipped files are placed locally
local_pspl_folder <- paste0(substr(getwd(),1,1),':/data/data_projects/AR2022/PSPL/gdb_data')

# copy all the zips
f_list <- list.files(ftp_pspl_folder, full.names = TRUE)

# subset for testing
#f_list <- f_list[1:4]

file.copy(f_list, local_pspl_folder)

```

Unzip the Gdb files

```{r unzip}
# get a list of the zip file names
zipF <- list.files(local_pspl_folder,full.names = TRUE)

# unzip
a <- lapply(zipF,FUN=unzip,exdir = local_pspl_folder)

# delete the zip files
b <- lapply(zipF,FUN=file.remove)


```

End of GDB Load




End: `r format(Sys.time(),"%c")`




