---
title: "PostgreSQL Point Intersect 1.0"
author: "D. Waddell"
date: "`r Sys.Date()`"
output: md_document
---

## VRI spatial intersect with PSPL points 


Assumes veg_comp_spatial exists.  
assumes that the PSPL points have been loaded: unit 1.. unit n




Start: `r Sys.time()`

```{r read_data}


year <- '2022'


library(RPostgreSQL)

# set up for load to PostgreSQL
# schema must include public for geom functions to work.
schema <- paste0('msyt_',year,',public')
opt <- paste0("-c search_path=",schema)
user_name <- 'results'
database <- 'msyt'




# this is where the unzipped files are placed locally
local_pspl_folder <- paste0(substr(getwd(),1,1),':/data/data_projects/AR2022/PSPL/gdb_data')

# build list of the PSPL gdbs
# list of gdb files to process
f_list <- list.files(local_pspl_folder,full.names = TRUE)

#number of files to process
num_units = length(f_list)


```

```{r}

con <- dbConnect('PostgreSQL',dbname=database,user=user_name,options=opt)

# pre delete 
q1 <- 'drop table if exists pspl_fid_merged'
dbExecute(con,q1)


q1 <- 'create table pspl_fid_merged 
(
 feature_id integer,
 id_tag     text,
 at_si      real,
 ba_si      real,
 bg_si      real,
 bl_si      real,
 cw_si      real,
 dr_si      real,
 ep_si      real,
 fd_si      real,
 hm_si      real,
 hw_si      real,
 lt_si      real,
 lw_si      real,
 pa_si      real,
 pl_si      real,
 pw_si      real,
 py_si      real,
 sb_si      real,
 se_si      real,
 ss_si      real,
 sw_si      real,
 sx_si      real,
 yc_si      real,
 unit_no    integer
 )'
 
 
dbExecute(con,q1)

dbDisconnect(con)



```




## process each point table 

Note that the intersection is using st_contains(vri,point).  

This may fail in what is expected to be a very small subset it the point falls exactly on the vri polygon line.

There are examples where the PSPL point is OUTSIDE the VRI boundary.  

Arrow, Arrowsmith as examples.  

Ignore these and move on.  

id_tag = 01_082F_16203_04799




```{r intersect,eval=TRUE, echo=FALSE, message=FALSE}

# the call to the psql interactive needs the schema assigned
  # define the schema via options
  db <- paste0('dbname=',database,' options=--search_path=',schema)
  # force a quoted string
  db <- shQuote(db)
  
  
# set this up as a function

run_sql <- function(fn,unit_name,number){
  
  #system2("psql",args=c('-d',db,'-U',user_name,'-f',fn,'-v',x1,'-v',x2,'-v',no),stderr=TRUE)
  system2("psql",args=c('-d',db,'-U',user_name,'-f',fn,'-v',unit_name,'-v',number),stderr=TRUE)
  
}


for (i in 1:num_units){  
  
    # i <- 1
      
      # input unit name
      name1 <- c("pspl_unit")
      unit <- paste0("unit=",name1,i)
      
      # unit name after intersect
      #name2 <- paste("pspl_fid_unit")
      #table <- paste0("sp=",name2,i)
      
      # unit number
      unit_no <- paste0("unit_no=",i)
    
      run_sql('2_02_intersect_fid.sql',unit,unit_no)
      
}



```


End: `r Sys.time()`


