---
title: "PSPL GDB Point Load to PostgreSQL"
author: "D. Waddell"
date: "`r Sys.Date()`"
output: md_document
---

## Import from GDB to PostgreSQL

Compare 2 methods

- gdal_utils.vectortranslate
- use GDAL OGR2OGR (installed)

  

Start: `r Sys.time()`

```{r read_data}


year <- '2022'

library(sf)
library(RPostgreSQL)


# set up for load to PostgreSQL
schema <- paste0('msyt_',year)
opt <- paste0("-c search_path=",schema)
user_name <- 'postgres'
database <- 'msyt'
con <- dbConnect('PostgreSQL',dbname=database,user=user_name,options=opt)


# this is where the unzipped files are placed locally
local_gdb_folder <- paste0(substr(getwd(),1,1),':/data/data_projects/AR2022/PSPL/gdb_data')

# build list of the PSPL gdbs
# list of gdb files to process
f_list <- list.files(local_gdb_folder,full.names = TRUE)
num_gdb = length(f_list)  #number of files to process



```



## process each gdb 

- Read each GDB
- export to PostgreSQL


## Load using sf::gdal_utils.gdaltranslate

This will bring any NULL values in the GDB as actual NULL in PostgreSQL.


```{r load_gdal_utils, eval = TRUE}

gdal_utils_gdb_load <- function(pf,n){

  # n <- 1
  # pf <- f_list[1]
  
  # PostgreSQL connection settings
  # schema is not defined
  dest <- c("PG:dbname=msyt user=results")
  
  gdb_fc <- tools::file_path_sans_ext(basename(pf))
  
  # give new layer name the schema name 
  new_layer <- paste0('msyt_',year,'.pspl_unit',n)
  
  
  # Options Notes
  # spatial index is required
  # set geometry name to wkb_geometry
  
  gdal_utils(
    util="vectortranslate",
    source=pf,
    dest,
    options=
      c('-a_srs','EPSG:3005',
        '-gt','10000',
        '-nln',new_layer,
        '-lco', 'GEOMETRY_NAME=wkb_geometry',
        '-overwrite'
        )
    )
  

}

```


# alternative load OGR2OGR

ogr2ogr -f "PostgreSQL" PG:"dbname=msyt" Site_Prod_100_Mile_House.gdb Site_Prod_100_Mile_House --debug ON



- ogr2ogr -a_srs EPSG:3005 -nln test1 -gt 200000 --config PG_USE_COPY YES -lco GEOMETRY_NAME=wkb_geometry -f PostgreSQL PG:"dbname=msyt user=results" Site_Prod_100_Mile_House.gdb Site_Prod_100_Mile_House

Note: If you get the following message when doing a psql> \d table   
ERROR:  column c.relhasoids does not exist  
Your client is wrong.  
Change to client that matches your PostreSQL version.

```{r}

ogr_load <- function(pf,n){
  
  
  # pf = GDB full name
  
  # give new layer name the schema name 
  new_layer <- paste0('msyt_',year,'.pspl_ogr2ogr_unit',n)
  gdb_fc <- tools::file_path_sans_ext(basename(pf))  
  
  ogr1 <- paste0("-a_srs EPSG:3005 -gt 100000 ")
  ogr2 <- paste0("-f PostgreSQL \"PG:dbname='msyt' user='results'\" -nln  ")
  ogr_cmd <- paste0(ogr1,ogr2,new_layer,' ',pf,' ',gdb_fc,' -lco ', 'GEOMETRY_NAME=wkb_geometry',' -overwrite')

  system2("ogr2ogr",args=ogr_cmd,wait=TRUE,stderr=TRUE)
  
}


```


```{r load_all_units}


# creates unit1 .. unitxx depending on the number of GDBs
  # unit1 does NOT refer to tsa 01
  # it is simply a reference number
if(length(f_list) ==0 ) { print("file list EMPTY")}

# initialize the counter
n <- 1


#process the file list
for(f in f_list){
      
  a <- gdal_utils_gdb_load(f,n)
  #b <- ogr_load(f,n)
  
  n <- n + 1
      
}



```


```{r ending}





dbDisconnect(con)


```


End: `r Sys.time()`


