---
title: "Coparing 4 rasterize methods"
author: "D. Waddell"
date: "`r Sys.Date()`"
output: md_document
---


Develop a standardized approach to rasterization for FAIB data processing.  


### Method 1: GDB to TIF using sf::gdal_utils

Using only R-4.1.3 
Package: sf  

No GDAL or Python installed.  

Workstation config: 32GB RAM  


Rasterize VRI from GDB 
Previously impossible on 32 GB machine using R.  

sf::gdal_utils relies on backed C++ gdal rasterize function.  
This relieves the memory load from R.  




Reads: D:/data/data_projects/AR2022/vri/VEG_COMP_LYR_R1_POLY_2021.gdb  


Note that the supplied file is extracted from:
https://catalogue.data.gov.bc.ca/dataset/vri-2020-forest-vegetation-composite-layer-1-l1-  


Publication date: 2021-02-08  

Start: `r Sys.time()`

```{r read_gdb}


library(sf)
library(terra)


# read gdb file

src <- 'D:/data/data_projects/AR2022/vri/VEG_COMP_LYR_R1_POLY_2021.gdb'
dest <- paste0(substr(getwd(),1,1),':/data/data_projects/VRI_Rasterization/method1.tif')


gdal_utils("rasterize",src,dest,options = 
             c('-tr','100',' 100',
                '-te','159587.5 ','173787.5 ','1881187.5 ','1748187.5',
                '-ot', 'UInt32 ',
                '-l', 'VEG_COMP_LYR_R1_POLY',
                '-a', 'FEATURE_ID' ,
                '-a_srs','EPSG:3005',
                '-a_nodata', '0',
                '-co','COMPRESS=LZW'),
                '-overwrite')


```

End Method 1 GDB -> Tif: `r Sys.time()`


## Method 2: PostgreSQL to TIF using sf::gdal_utils

```{r read_postgresql}


src <- "PG:dbname='msyt' user='postgres'"
spatial_table <- 'msyt_2022.veg_comp_spatial'
dest <- paste0(substr(getwd(),1,1),':/data/data_projects/VRI_Rasterization/method2.tif')


gdal_utils("rasterize",src,dest,options = 
             c('-tr','100',' 100',
                '-te','159587.5 ','173787.5 ','1881187.5 ','1748187.5',
                '-ot', 'UInt32 ',
                '-l', spatial_table,
                '-a', 'FEATURE_ID' ,
                '-a_srs','EPSG:3005',
                '-a_nodata', '0',
                '-co','COMPRESS=LZW'),
                '-overwrite')

```

End Method 2 PostgreSQL -> Tif: `r Sys.time()`

## Method 3: gdal_rasterize GDB

Requires installation of GDAL and resetting of ENV  

```{r gdal_rasterize_gdb}

src <- 'D:/data/data_projects/AR2022/vri/VEG_COMP_LYR_R1_POLY_2021.gdb'
dest <- paste0(substr(getwd(),1,1),':/data/data_projects/VRI_Rasterization/method3.tif')


cmd <- paste0(c('-tr','100',' 100',
                '-te','159587.5 ','173787.5 ','1881187.5 ','1748187.5',
                '-ot', 'UInt32 ',
                '-l', 'VEG_COMP_LYR_R1_POLY',
                '-a', 'FEATURE_ID' ,
                '-a_srs','EPSG:3005',
                '-a_nodata', '0',
                '-co','COMPRESS=LZW',src,dest))

gdal_rasterize <- 'C:/Program Files/GDAL/gdal_rasterize.exe'

system2(gdal_rasterize,args=cmd,wait=TRUE,stderr = TRUE)

```

End Method 3 gdal_rasterize GDB: `r Sys.time()`

## Method 4: gdal_rasterize PostgreSQL

Requires installation of GDAL and resetting of ENV  

```{r gdal_rasterize}


src <- shQuote("PG:dbname='msyt' user='postgres'")
spatial_table <- 'msyt_2022.veg_comp_spatial'
dest <- paste0(substr(getwd(),1,1),':/data/data_projects/VRI_Rasterization/method4.tif')

cmd <- paste0(c('-tr','100',' 100',
                '-te','159587.5 ','173787.5 ','1881187.5 ','1748187.5',
                '-ot', 'UInt32 ',
                '-l', spatial_table,
                '-a', 'FEATURE_ID' ,
                '-a_srs','EPSG:3005',
                '-a_nodata', '0',
                '-co','COMPRESS=LZW',src,dest))

# point to the EXE
gdal_rasterize <- 'C:/Program Files/GDAL/gdal_rasterize.exe'

system2(gdal_rasterize,args=cmd,wait=TRUE,stderr = TRUE)

```
End Method 4 gdal_rasterize PostgreSQL: `r Sys.time()`

```{r fasterize, eval=FALSE}


#Simple database connectivity functions
getSpatialQuery<-function(sql){
  conn<-DBI::dbConnect(dbDriver("PostgreSQL"),
                       dbname='msyt', 
                       user='postgres' ,
                       )
  
  on.exit(dbDisconnect(conn))
  st_read(conn, query = sql)
}

#Get dummy layer for projection (too lazy to write it) 
lyr<-getSpatialQuery(paste("SELECT geom FROM public.gcbp_carib_polygon"))

#Make an empty provincial raster aligned with hectares BC
ProvRast <- raster(
  nrows = 15744, ncols = 17216, xmn = 159587.5, xmx = 1881187.5, ymn = 173787.5, ymx = 1748187.5, 
  crs = st_crs(lyr)$proj4string, resolution = c(100, 100), vals = 0
)

layer<-getSpatialQuery("SELECT feature_id, shape FROM public.veg_comp_lyr_r1_poly2021")

layer.ras <-fasterize::fasterize(sf= layer, raster = ProvRast , field = "feature_id")
rm(layer)
gc()

writeRaster(layer.ras, file="vri2021_id.tif", format="GTiff", overwrite=TRUE)

```


End: `r Sys.time()`


