---
title: "Comparing 5 rasterize methods"
author: "D. Waddell"
date: "`r Sys.Date()`"
output: md_document
---


Develop a standardized approach to rasterization for FAIB data processing.  


### Method 1: GDB to TIF using sf::gdal_utils

Using only R-4.1.3 
Package: sf  

No GDAL or Python installed.  

Workstation config: 32GB RAM  


Rasterize VRI from GDB 
Previously impossible on 32 GB machine using R.  

sf::gdal_utils relies on backed C++ gdal rasterize function.  
This relieves the memory load from R.  

Links to: GEOS 3.9.1, GDAL 3.2.1, PROJ 7.2.1; sf_use_s2() is TRUE




Reads: D:/data/data_projects/AR2022/vri/VEG_COMP_LYR_R1_POLY_2021.gdb  


Note that the supplied file is extracted from:

catalogue.data.gov.bc.ca/dataset

search for : veg_comp_lyr_r1_poly


Publication date: 2021-02-08  (which is wrong by the way), which should actually be 2022

Start: `r Sys.time()`

```{r read_gdb}


library(sf)
library(terra)
library(RPostgreSQL)
library(raster)


# read gdb file

src <- 'D:/data/data_projects/AR2022/vri/VEG_COMP_LYR_R1_POLY_2021.gdb'
dest <- paste0(substr(getwd(),1,1),':/data/data_projects/VRI_Rasterization/method1.tif')


gdal_utils("rasterize",src,dest,options = 
             c('-tr','100',' 100',
                '-te','159587.5 ','173787.5 ','1881187.5 ','1748187.5',
                '-ot', 'UInt32',
                '-l', 'VEG_COMP_LYR_R1_POLY',
                '-a', 'FEATURE_ID' ,
                '-a_srs','EPSG:3005',
                '-a_nodata', '0',
                '-co','COMPRESS=LZW'),
                '-overwrite')


```

End Method 1 GDB -> Tif: `r Sys.time()`


## Method 2: PostgreSQL to TIF using sf::gdal_utils

Links to a local PostgreSQL database that used an Oracle Foreign data wrapper to create a copy of idwprod1.veg_comp_lyr_r1_poly.  PostgreSQL table is called veg_comp_spatial and only contains feature_id and wkb_geometry. 

```{r read_postgresql}


src <- "PG:dbname='msyt' user='postgres'"
spatial_table <- 'msyt_2022.veg_comp_spatial'
dest <- paste0(substr(getwd(),1,1),':/data/data_projects/VRI_Rasterization/method2.tif')


gdal_utils("rasterize",src,dest,options = 
             c('-tr','100',' 100',
                '-te','159587.5 ','173787.5 ','1881187.5 ','1748187.5',
                '-ot', 'UInt32',
                '-l', spatial_table,
                '-a', 'FEATURE_ID' ,
                '-a_srs','EPSG:3005',
                '-a_nodata', '0',
                '-co','COMPRESS=LZW'),
                '-overwrite')

```

End Method 2 PostgreSQL -> Tif: `r Sys.time()`

## Method 3: gdal_rasterize GDB

Uses an installed GDAL gdal_rasterize.ex.   
GDAL 3.5.1, released 2022/06/30  
Requires installation of GDAL and resetting of ENV  

```{r gdal_rasterize_gdb}

src <- 'D:/data/data_projects/AR2022/vri/VEG_COMP_LYR_R1_POLY_2021.gdb'
dest <- paste0(substr(getwd(),1,1),':/data/data_projects/VRI_Rasterization/method3.tif')


cmd <- paste0(c('-tr','100',' 100',
                '-te','159587.5 ','173787.5 ','1881187.5 ','1748187.5',
                '-ot', 'UInt32',
                '-l', 'VEG_COMP_LYR_R1_POLY',
                '-a', 'FEATURE_ID' ,
                '-a_srs','EPSG:3005',
                '-a_nodata', '0',
                '-co','COMPRESS=LZW',src,dest))

gdal_rasterize <- 'C:/Program Files/GDAL/gdal_rasterize.exe'

system2(gdal_rasterize,args=cmd,wait=TRUE,stderr = TRUE)

```

End Method 3 gdal_rasterize GDB: `r Sys.time()`

## Method 4: gdal_rasterize PostgreSQL

Uses gdal_rasterize.exe (installed)  
Connects to local PostgreSQL database.  

```{r gdal_rasterize}


src <- shQuote("PG:dbname='msyt' user='postgres'")
spatial_table <- 'msyt_2022.veg_comp_spatial'
dest <- paste0(substr(getwd(),1,1),':/data/data_projects/VRI_Rasterization/method4.tif')

cmd <- paste0(c('-tr','100',' 100',
                '-te','159587.5 ','173787.5 ','1881187.5 ','1748187.5',
                '-ot', 'UInt32',
                '-l', spatial_table,
                '-a', 'FEATURE_ID' ,
                '-a_srs','EPSG:3005',
                '-a_nodata', '0',
                '-co','COMPRESS=LZW',src,dest))

# point to the EXE
gdal_rasterize <- 'C:/Program Files/GDAL/gdal_rasterize.exe'

system2(gdal_rasterize,args=cmd,wait=TRUE,stderr = TRUE)

```
End Method 4 gdal_rasterize PostgreSQL: `r Sys.time()`


## Method 5: fasterize

Included for information only.  

The R package fasterize offers very fast rasterization.  However, memory requirements for the routine require over 50GB of RAM for the process to run to completion.  



```{r fasterize, eval=FALSE}



#Simple database connectivity functions
getSpatialQuery<-function(sql){
  conn <- dbConnect("PostgreSQL",
                       dbname='msyt', 
                       user='postgres' ,
                       )
  
  on.exit(dbDisconnect(conn))
  st_read(conn, query = sql)
  
}


# Make an empty provincial raster aligned with hectares BC
# create SpatRaster so crs can be set
ProvRast <- rast(
  nrows = 15744, ncols = 17216, xmin = 159587.5, xmax = 1881187.5, ymin = 173787.5, ymax = 1748187.5, 
  crs = 'epsg:3005', resolution = c(100, 100), vals = 0
)

# convert to raster so that fasterize can be used
ProvRast <- raster(ProvRast)

layer<-getSpatialQuery("SELECT feature_id, wkb_geometry FROM msyt_2022.veg_comp_spatial")

layer.ras <-fasterize::fasterize(sf= layer, raster = ProvRast , field = "feature_id")
rm(layer)
gc()

tif_name <- 'D:/data/data_projects/VRI_Rasterization/tif_from_fasterize.tif'
writeRaster(layer.ras, file=tif_name, format="GTiff", datatype='INT4U', overwrite=TRUE)

```


End: `r Sys.time()`


