---
title: "Compare 2 TIFs"
author: "D. Waddell"
date: "`r Sys.Date()`"
output: md_document
---

Check that what Iaian produced for the official vri feature_id Tif matches the method checks comparing sf::gdal_utils to gdal_rasterize.exe  

File provided by Iaian:  veg_comp_lyr_r1_poly_internal_2021.tif  

Note that Iaian's tif had a chunk of Alberta in it.  
This needs to be masked out.

## Create a mask using QGis

- bring up the raster in QGis
- zoom to the area that needs to be masked
- Layer / Create Layer / New ShapeFile Layer
- give it a file name
- add a field (called id)
- set geometry type to polygon
- set CRS to EPSG:3005
- Shp will appear in Layers list
- Select that layer
- Select Edit mode
- Use Add Polygon Feature
  - Left click to add points, right click to finish
- Toggle off edits and save file

```{r}



library(sf)
library(terra)
library(RPostgreSQL)
library(raster)
library(kableExtra)

del_file <- function (fn){
  
  #Check its existence
  if (file.exists(fn)) {
    #Delete file if it exists
    file.remove(fn)
  }
}
  



# created a mask to get rid of Alberta blob.
# read gdb file
# data has single polygon with id = 101


# standardize extents
xmin <- 273287.5
xmax <- 1870587.5
ymin <- 367787.5
ymax <- 1735787.5

nodata <- 0

dataType <- 'Int32'


# raster files
src <- 'D:/data/data_projects/AR2022/base/vri_mask.shp'
dest <- 'D:/data/data_projects/AR2022/base/vri_mask_for_delete.tif'

del_file(dest)

# note that in reading a Shp file, the layer is the same as the file name

gdal_utils("rasterize",src,dest,options = 
             c('-tr','100',' 100',
                '-te',xmin,ymin,xmax,ymax,
                '-ot', dataType,
                '-l', 'vri_mask',
                '-a', 'id' ,
                '-a_srs','EPSG:3005',
                '-a_nodata', nodata,
                '-co','COMPRESS=LZW'),
                '-overwrite')

# update for NA
mask_raster <- terra::rast(dest)

# change NoData to 1 for masking
# we want the invert of the outline polygon so that it can be deleted from orginal data
mask_raster[is.na(mask_raster)]  <- 1

# change wher there are values to NA to use as mask to get rid of this from Iaian's data
mask_raster[mask_raster != 1]  <- NA

# the mask will have 1 for valid rasters and NoData where we want to mask out
# so in effect we have blanked out the polygon defined in the Shp file


del_file(dest)

terra::writeRaster(mask_raster, dest, datatype='INT4U', overwrite=TRUE)

# read Iaian's tif and apply the mask

vri_in <- 'D:/data/data_projects/AR2022/base/veg_comp_lyr_r1_poly_internal_2021.tif'
vri_out <- 'D:/data/data_projects/AR2022/base/veg_comp_2022_masked.tif'

base_raster <- terra::rast(vri_in)

# apply the mask
base_raster_masked <- mask(base_raster,mask_raster)

# update the NoData to zeros
base_raster_masked[is.na(base_raster_masked)]  <- 0


del_file(vri_out)
terra::writeRaster(base_raster_masked, vri_out, datatype='INT4U', overwrite=TRUE)

```

## now that the mask has been applied we can compare


```{r eval=TRUE}

# read each raster set and compare

# if the diff is not zero, set it to 1
# this will show where pixel values are different

tif1 <- 'D:/data/data_projects/VRI_Rasterization/method1.tif'
tif2 <- 'D:/data/data_projects/AR2022/base/veg_comp_lyr_r1_poly_internal_2021.tif'
tif3 <- 'D:/data/data_projects/AR2022/base/veg_comp_2022_masked.tif'

r1 <- terra::rast(tif1)
r3 <- terra::rast(tif3)

names(r1) <- 'method1'
names(r3) <- 'vri_masked'

# get list of unique feature ids
v_r1 <- unique(as.data.frame(values(r1)))
names(v_r1) <- 'feature_id'

v_r3 <- unique(as.data.frame(values(r3)))
names(v_r3) <- 'feature_id'




c1 <- r1 - r3
c1[c1 != 0] <- 1

f1 <- as.data.frame(terra::freq(c1))
f1 <- f1[,2:3]


kable(f1)


```

Table 1. Differences

Number of differences: `r f1$count[f1$value==1]`


```{r build_brick}

# create list of rasters
lst <- list(r1,base_raster,base_raster_masked,c1)


# create a brick of these rasters from list
raster_brick <-terra::rast(lst)

# name the layers
names(raster_brick) <- c('method1','vri_base','vri_base_masked','diff')

# write brick to a tiff
tif_brick <- 'D:/data/data_projects/AR2022/base/tif_brick.tif'

del_file(tif_brick)

terra::writeRaster(raster_brick, tif_brick, datatype='INT4U', overwrite=TRUE)


# write the differences to a separate tif
diff_1 <- 'D:/data/data_projects/AR2022/base/tif_diff.tif'

del_file(diff_1)

terra::writeRaster(c1, diff_1, datatype='INT4U', overwrite=TRUE)



```


```{r}


# can write to points to have a look
point_file <- 'D:/data/data_projects/AR2022/base/tif_diff.tif'

pr <- terra::rast(point_file)

# set 0 to NA
pr[pr==0] <- NA

p <- terra::as.points(pr,values=TRUE,na.rm=TRUE)

# write to shape
f_out <- 'D:/data/data_projects/AR2022/base/tif_diff_points.shp'

del_file(f_out)

writeVector(p,f_out,overwrite=TRUE)



```


# Cross Check

All data that is produced neesds to be checked against the list of feature_ids found in the vri.  

```{r echo=FALSE,message=FALSE,warning=FALSE}


con <- dbConnect('PostgreSQL',dbname='msyt')

fid <- dbGetQuery(con,'select feature_id from msyt_2022.veg_comp')
dbDisconnect(con)

# method 1

# get unique values from r1 - r3

new_fid_r1 <- v_r1 %>% subset(!feature_id %in% fid$feature_id)

new_fid_r3 <- v_r3 %>% subset(!feature_id %in% fid$feature_id)

kable(new_fid_r1)
kable(new_fid_r3)




```
