---
title: "Compare TIFs"
author: "D. Waddell"
date: "`r Sys.Date()`"
output: html_document
---

```{r}


# raster files
tif_method1 <- 'D:/data/data_projects/VRI_Rasterization/method1.tif'
tif_method2 <- 'D:/data/data_projects/VRI_Rasterization/method2.tif'
tif_method3 <- 'D:/data/data_projects/VRI_Rasterization/method3.tif'
tif_method4 <- 'D:/data/data_projects/VRI_Rasterization/method4.tif'
tif_method5 <- 'D:/data/data_projects/VRI_Rasterization/tif_fasterize.tif'

tif_brick <- 'D:/data/data_projects/VRI_Rasterization/tif_brick.tif'

# read each raster set and compare

# if the diff is not zero, set it to 1
# this will show where pixel values are different


r1 <- terra::rast(tif_method1)

# compare 1 to 2

r2 <- terra::rast(tif_method2)

c1 <- r1 - r2
c1[c1 != 0] <- 1

f1 <- terra::freq(c1)
f1

```

Table 1.  Compare sf::gdal_utils.rasterize GDB to PostgreSQL

This table shows there are 31 features that are different.  

Both methods use sf::gdal_utils.rasterize.  
Except one points at a GDB as source.   
The other points at PostgreSQL as source.  



```{r}

# compare 1 to 3
r3 <- terra::rast(tif_method3)


c1 <- r1 - r3
c1[c1 != 0] <- 1

# differences
# 0 = no difference
# 1 = difference of 1
# 2 = difference greater than 1

f2 <- terra::freq(c1)
f2

```

Table 2.  Compare sf::gdal_utils.rasterize (GDB) to gdal_rasterize.exe GDB

This table shows that the 2 TIFs are identical.  


```{r}

# compare 2 to 4
r4 <- terra::rast(tif_method4)

c1 <- r2 - r4
c1[c1 != 0] <- 1

f3 <- terra::freq(c1)
f3

```

Table 3. Compare sf::gdal_utils.rasterize (PostgreSQL) to gdal_rasterize.exe GDB

This table shows that the 2 TIFs are identical.  


```{r eval=TRUE}
# compare 1 to 4
r5 <- terra::rast(tif_method5)

# force projection
terra::crs(r5) <- 'epsg:3005'


# use absolutes
c1 <- abs(r1 - r5)

# where the difference is 1 assign 2
c1[c1 == 1] <- 1

# where there is a difference of more thatn 1
c1[c1 > 1 ] <- 2

f4 <- terra::freq(c1)
f4




```

Table 4:  Compare sf::gdal_utils.rasterize to fasterize

This table shows that there are some differences between fasterize and the other rasterize techniques.   

- 0 means NO difference
- 1 means a difference of 1
- 2 means a entirely different


```{r eval=TRUE}
# compare 1 to 5 with masking
#r6 <- terra::rast(tif_method5)



# land / water mask supplied by Mike F.
w1 <- paste0(substr(getwd(),1,1),':/data/data_projects/base_data/land_water.tif')
mask_raster <- terra::rast(w1)

# this mask is a 0/1 of land water
# there are values of 0 between Vancouver Island and the mainland.
# these need to be set to NA to be used as a land mask
# set values in mask to NA where 0
mask_raster[mask_raster==0] <- NA

# force the CRS
terra::crs(mask_raster ) <- 'epsg:3005'

# need to change existing 0 to NA to match r1 and r2
#r5[r5 == 0] <- NA



# apply the land mask to the base layer
# filter out the water
r1_masked <- terra::mask(r1,mask_raster)

# filter out any zeros
# set to NA
r1_masked[r1_masked==0] <- NA

# apply the land mask to the fasterized tif
# filter out the water
r5_masked <- terra::mask(r5,mask_raster)




# set no data to 0 in the base tif
# this will include water and any isolated nodata values inside land
#r5[is.na(r5)] <- 0



# filter out any zeros
# set to NA
r5_masked[r5_masked==0] <- NA




#c1 <- r1 - r5

# use absolutes
c5 <- abs(r1 - r5)

# where the difference is 1 assign 2
c5[c5 == 1] <- 1

# where there is a difference of more thatn 1
c5[c5 > 1 ] <- 2

f5 <- terra::freq(c5)
f5

#terra::writeRaster(c1,tif_compare,datatype='INT2U')



```

Table 5:  Compare sf::gdal_utils.rasterize to fasterize Mask applied to both

This table shows that there are some differences between fasterize and the other rasterize techniques.   

- 0 means NO difference
- 1 means a difference of 1
- 2 means a entirely different
```{r brick}

# build a raster brick of all the differences.

r5 <- terra::rast(tif_method5)

# create list of rasters
lst <- list(r1,r2,r3,r4,r5)

# create a brick of these rasters from list
raster_brick <-terra::rast(lst)

# write brick to a tiff

terra::writeRaster(raster_brick, tif_brick, datatype='INT4U', overwrite=TRUE)




```


```{r}

# write the fasterize compare to a tif

diff_tif <- 'D:/data/data_projects/VRI_Rasterization/tif_diff.tif'
terra::writeRaster(c1, diff_tif, datatype='INT4U', overwrite=TRUE)

```



## Discussion

The first 4 methods seem to line up quite well.  The differences between the GDB and PostgreSQL as source come from the interpretation of a 45degree line bisecting the raster.  One method goes left, the other goes right. Comparing athe 2 GDB reads and the 2 PostgreSQL reads, they are identical.  There is only a difference when comparing between the GDB and PostgreSQL reads.

The fasterize raster did not line up quite so well.  I have had to force the projection to epsg:3005 in the fasterized tif.  I also had to apply the land_water mask before I could make the tifs line up.   

I'm thinking that part of the problem with fasterize is that it requires a template raster before generating the tif.  Here a zero filled PROV raster is being used.  Not sure if this is creating some of the differences.

Fasterize requires 64GB of RAM to be able to complete this task.  IT will NOT run on a 32GB machine.

As to which method is best, it is more of a personal preference.  The first 2 methods mean the OSGEO/GDAL does NOT need to be installed on a users machine.  It also means that there are no ENV requirements that need to be updated.  From a drop on an analysts desk point of view, the first 2 methods are simpler.  

The third and fourth methods require an install of GDAL and also require an update to the ENV to locate all the software components.  This needs to be updated every time GDAL changes.

The fifth method requires some further investigation.  The projection and no data values need to be evaluated. And it needs 64GB of RAM.



