---
title: "Coparing 4 rasterize methods"
author: "D. Waddell"
date: "`r Sys.Date()`"
output: md_document
---



```{r}

library(raster)
library(terra)



row <- 15744
col <- 17216

max_no <- row * col

# terra
ProvRast <- rast(nrows = row, ncols = col, 
                xmin = 159587.5, xmax = 1881187.5, 
                ymin = 173787.5, ymax = 1748187.5, 
                crs='epsg:3005',
                resolution = c(100, 100), 
                vals = NA )
                
t1  <- ProvRast   
t1[100]<-17840065
freq(t1) 

t1[!is.na(t1)]


```

Using terra object PsatRaster:  
Here we have set 1 SpatRaster element to 17840065


```{r}

# raster
ProvRast2<-raster(nrows=15744, ncols=17216, xmn=159587.5, xmx=1881187.5,
                 ymn=173787.5, ymx=1748187.5, 
                 #crs="+proj=aea +lat_1=50 +lat_2=58.5 +lat_0=45 +lon_0=-126 +x_0=1000000 +y_0=0 +datum=NAD83 +units=m +no_defs +ellps=GRS80 +towgs84=0,0,0",
                 crs= "+proj=aea +lat_1=50 +lat_2=58.5 +lat_0=45 +lon_0=-126 +x_0=1000000 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs", 
                 resolution = c(100,100), vals = NA)



t2<-ProvRast2
t2[100]<-17840065
freq(t2)

t2[!is.na(t2)]

```

Using a raster object:  
Again, we have set 1 RasterLayer element to 17840065

```{r}

writeRaster(t1, file="c:/data/test1.tif", datatype = 'INT4U', overwrite=TRUE)
writeRaster(t2, file="c:/data/test2.tif", datatype = 'INT4U', overwrite=TRUE)


test1 <- rast('C:/data/test1.tif')
test2 <- raster('C:/data/test2.tif')

```

Write then read the Tif files

```{r}

freq(test1)

test1[!is.na(test1)]

```

Here is the frequency of the Tif SpatRaster elements.  

Note that 17840065 has changed to 17840064     




```{r}



test1

```

But if we look at the SpatRaster itself we see:

Min max values of 17840065

```{r}

freq(test2)

test2[!is.na(test2)]

test2



```

and the same happens for the RasterLayer when read from Tif  

## Note

using freq() returns 17840064  
whereas the actual data within the raster is 17840065  

```{r}

identical(test1,test2)



```