---
title: "PSPL Site Index Conversion"
output: md_document
---


# PSPL Method 2022  

## Feature_id processing 

- run SI conversion on feature_id based si
- run SI conversion on opening_id based si
- run SI conversion on BEC based si 



Create the following tables:

- pspl_bec_site_index
- pspl_fid_site_index
- pspl_op_site_index


Start: `r format(Sys.time(),"%c")`

```{r setup, echo=TRUE,message=TRUE,warning=TRUE}

library(RPostgreSQL)
library(tidyverse)
library(data.table)
library(ggplot2)

# set up for schema and user
schema <- 'msyt_2022'
opt <- paste0("-c search_path=",schema)
user_name <- 'postgres'
database <- 'msyt'
con <- dbConnect('PostgreSQL',dbname='msyt',user=user_name,options=opt)


#load the R code for site index conversions

si_convert <- paste0(getwd(),'/site_index_conversion_equations_v2.r')
source(si_convert, local = knitr::knit_global())


```



### Feature_id Site Index Conversions

Run the SI conversion on avg_fid_data.   

mean value data by feature



```{r  si_convert_fid,echo=TRUE,message=TRUE,warning=TRUE}


# read avg_fid_data: table = pspl_fid_site_index_pre_convert
# this is the mean value feature_id data

q1 <- 'select *  from msyt_2022.pspl_fid_site_index_pre_convert'
avg_fid_data <- dbGetQuery(con,q1)
 

setDT(avg_fid_data)

# note that si_convert required 0 in place of NA
# si_convert will handle this


# run the SI conversions
avg_fid_data <- si_convert(avg_fid_data)


# write the data
file_name <- paste0(substr(getwd(),1,1),':/data/data_projects/AR2022/PSPL/si_data/pspl_fid_site_index_post_convert.csv')
fwrite(avg_fid_data, file_name, col.names=TRUE, row.names=FALSE, quote = FALSE, sep=",")


tbl_name <- paste0('pspl_fid_site_index_post_convert')

# pre delete table
if(dbExistsTable(con,tbl_name)) {
  dbRemoveTable(con,tbl_name)
}

# write to table

dbWriteTable(con,tbl_name,avg_fid_data,row.names = FALSE)

```



### run SI conversion on the bec means values


- run SI conversion on BEC based si 

```{r bec_si_convert}

# read avg_BEC_data: table = psql_bec_site_index_pre_convert
q1 <- 'select *  from msyt_2022.pspl_bec_site_index_pre_convert'
r1 <- dbSendQuery(con,q1)
avg_BEC_data <- dbFetch(r1,n=-1)

setDT(avg_BEC_data)


avg_BEC_data <- si_convert(avg_BEC_data)


# write the data
file_name <- paste0(substr(getwd(),1,1),':/data/data_projects/AR2022/PSPL/si_data/pspl_bec_site_index_post_convert.csv')
fwrite(avg_BEC_data, file_name, col.names=TRUE, row.names=FALSE, quote = FALSE, sep=",")


tbl_name <- paste0('pspl_bec_site_index_post_convert')


# pre delete table
if(dbExistsTable(con,tbl_name)) {
  dbRemoveTable(con,tbl_name)
}


# write to table
dbWriteTable(con,tbl_name,avg_BEC_data,row.names = FALSE)


```




## Conversion on Opening

```{r si_convert_op}



# read avg_op_data: table = pspl_op_site_index_pre_convert
q1 <- 'select *  from msyt_2022.pspl_op_site_index_pre_convert'
avg_op_data <- dbGetQuery(con,q1)

setDT(avg_op_data)



# run the conversion

avg_op_data <- si_convert(avg_op_data)

# writeout the post conversion file
file_name <-  paste0(substr(getwd(),1,1),':/data/data_projects/AR2022/PSPL/si_data/pspl_op_site_index_post_convert.csv')
fwrite(avg_op_data, file_name, col.names=TRUE, row.names=FALSE, quote = FALSE, sep=",")


# add src

avg_op_data$si_src <- 'PSPL'

tbl_name <- paste0('pspl_op_site_index_post_convert')

# pre delete table
if(dbExistsTable(con,tbl_name)) {
  dbRemoveTable(con,tbl_name)
}



dbWriteTable(con,tbl_name,avg_op_data,row.names = FALSE)


```


```{r cleanUp, eval=FALSE}


if(dbExistsTable(con,'pspl_fid_site_index_pre_convert')) {
  dbRemoveTable(con,'pspl_fid_site_index_pre_convert')
}

if(dbExistsTable(con,'pspl_op_site_index_pre_convert')) {
  dbRemoveTable(con,'pspl_op_site_index_pre_convert')
}

if(dbExistsTable(con,'pspl_bec_site_index_pre_convert')) {
  dbRemoveTable(con,'pspl_bec_site_index_pre_convert')
}

```


```{r discon}

dbDisconnect(con)

```



End: `r format(Sys.time(),"%c")`