---
title: "PSPL Stage3"
output:
  md_document:
    variant: gfm
---


# PSPL Method 2021  

## Feature_id processing 

- run SI conversion on feature_id based si
- run SI conversion on BEC based si 
- update feature_id si using BEc avg


Create the following tables:

- pspl_bec_site_index
- pspl_fid_site_index
- pspl_op_site_index


Start: `r format(Sys.time(),"%c")`

```{r setup, echo=TRUE,message=TRUE,warning=TRUE}

library(RPostgreSQL)
library(tidyverse)
library(data.table)
library(ggplot2)

# set up for schema and user
schema <- 'msyt_2021'
opt <- paste0("-c search_path=",schema)
user_name <- 'postgres'
database <- 'msyt'
con <- dbConnect('PostgreSQL',dbname='msyt',user=user_name,options=opt)


#load the R code for site index conversions
si_convert <- paste0(getwd(),'/site_index_conversion_equations.r')
source(si_convert, local = knitr::knit_global())

```



### Feature_id Site Index Conversions

Run the SI conversion on avg_fid_data.   

mean value data by feature



```{r  si_convert_fid,echo=TRUE,message=TRUE,warning=TRUE}


# read avg_fid_data: table = pspl_fid_site_index_pre_convert
# this is the mean value feature_id data

q1 <- 'select *  from msyt_2021.pspl_fid_site_index_pre_convert'
r1 <- dbSendQuery(con,q1)
avg_fid_data <- dbFetch(r1,n=-1)

setDT(avg_fid_data)

# note that si_convert required 0 in place of NA
# si_convert will handle this


# run the SI conversions
avg_fid_data <- si_convert(avg_fid_data)


# write the data
file_name <- 'D:/data/data_projects/PSPL_2021/pspl_fid_site_index_post_convert.csv'
fwrite(avg_fid_data, file_name, col.names=TRUE, row.names=FALSE, quote = FALSE, sep=",")


```



### run SI conversion on the bec means values


- run SI conversion on BEC based si 

```{r bec_si_convert}

# read avg_BEC_data: table = psql_bec_site_index_pre_convert
q1 <- 'select *  from msyt_2021.pspl_bec_site_index_pre_convert'
r1 <- dbSendQuery(con,q1)
avg_BEC_data <- dbFetch(r1,n=-1)

setDT(avg_BEC_data)


avg_BEC_data <- si_convert(avg_BEC_data)


# write the data
file_name <- 'D:/data/data_projects/PSPL_2021/pspl_bec_site_index.csv'
fwrite(avg_BEC_data, file_name, col.names=TRUE, row.names=FALSE, quote = FALSE, sep=",")

# pre delete table
if(dbExistsTable(con,'pspl_bec_site_index')) {
  db_drop_table(con,'pspl_bec_site_index')
}


# write to table
dbWriteTable(con,'pspl_bec_site_index',avg_BEC_data,row.names = FALSE)


```



## update converted using BEC converted


- update feature_id si using BEc avg


```{r update1,echo=TRUE,message=TRUE,warning=TRUE}


avg_fid_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), at_si := ifelse(at_si==0, i.at_si,at_si)]
avg_fid_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), ba_si := ifelse(ba_si==0, i.ba_si,ba_si)]
avg_fid_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), bg_si := ifelse(bg_si==0, i.bg_si,bg_si)]
avg_fid_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), bl_si := ifelse(bl_si==0, i.bl_si,bl_si)]
avg_fid_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), cw_si := ifelse(cw_si==0, i.cw_si,cw_si)]
avg_fid_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), dr_si := ifelse(dr_si==0, i.dr_si,dr_si)]
avg_fid_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), ep_si := ifelse(ep_si==0, i.ep_si,ep_si)]
avg_fid_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), fd_si := ifelse(fd_si==0, i.fd_si,fd_si)]
avg_fid_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), hm_si := ifelse(hm_si==0, i.hm_si,hm_si)]
avg_fid_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), hw_si := ifelse(hw_si==0, i.hw_si,hw_si)]
avg_fid_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), lt_si := ifelse(lt_si==0, i.lt_si,lt_si)]  
avg_fid_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), lw_si := ifelse(lw_si==0, i.lw_si,lw_si)]
avg_fid_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), pa_si := ifelse(pa_si==0, i.pa_si,pa_si)]
avg_fid_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), pl_si := ifelse(pl_si==0, i.pl_si,pl_si)]
avg_fid_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), pw_si := ifelse(pw_si==0, i.pw_si,pw_si)]
avg_fid_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), py_si := ifelse(py_si==0, i.py_si,py_si)]
avg_fid_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), sb_si := ifelse(sb_si==0, i.sb_si,sb_si)]
avg_fid_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), se_si := ifelse(se_si==0, i.se_si,se_si)]
avg_fid_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), ss_si := ifelse(ss_si==0, i.ss_si,ss_si)]
avg_fid_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), sw_si := ifelse(sw_si==0, i.sw_si,sw_si)]
avg_fid_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), sx_si := ifelse(sx_si==0, i.sx_si,sx_si)]
avg_fid_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), yc_si := ifelse(yc_si==0, i.yc_si,yc_si)]




```



```{r write_data}

# drop some columns
#avg_fid_data <- avg_fid_data #%>% select(-bec_zone,-bec_subzone)
setDT(avg_fid_data)

# add si_src
avg_fid_data$si_src <- 'PSPL'


# final output
file_name <- 'D:/data/data_projects/PSPL_2021/pspl_fid_site_index.csv'
fwrite(avg_fid_data, file_name, col.names=TRUE, row.names=FALSE, quote = FALSE, sep=",")


# pre delete table
if(dbExistsTable(con,'pspl_fid_site_index')) {
  db_drop_table(con,'pspl_fid_site_index')
}

# write to table
dbWriteTable(con,'pspl_fid_site_index',avg_fid_data,row.names = FALSE)


```


## Conversion on Opening

```{r si_convert_op}



# read avg_op_data: table = pspl_op_site_index_pre_convert
q1 <- 'select *  from msyt_2021.pspl_op_site_index_pre_convert'
r1 <- dbSendQuery(con,q1)
avg_op_data <- dbFetch(r1,n=-1)

setDT(avg_op_data)

# read BEC data
q2 <- 'select * from msyt_2021.pspl_bec_site_index'
r2 <- dbSendQuery(con,q2)
avg_BEC_data <- dbFetch(r2,n=-1)


# run the conversion

avg_op_data <- si_convert(avg_op_data)

# writeout the post conversion file
file_name <- 'D:/data/data_projects/PSPL_2021/pspl_op_site_index_post_convert.csv'
fwrite(avg_op_data, file_name, col.names=TRUE, row.names=FALSE, quote = FALSE, sep=",")



# update from BEC

avg_op_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), at_si := ifelse(at_si==0, i.at_si,at_si)]
avg_op_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), ba_si := ifelse(ba_si==0, i.ba_si,ba_si)]
avg_op_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), bg_si := ifelse(bg_si==0, i.bg_si,bg_si)]
avg_op_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), bl_si := ifelse(bl_si==0, i.bl_si,bl_si)]
avg_op_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), cw_si := ifelse(cw_si==0, i.cw_si,cw_si)]
avg_op_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), dr_si := ifelse(dr_si==0, i.dr_si,dr_si)]
avg_op_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), ep_si := ifelse(ep_si==0, i.ep_si,ep_si)]
avg_op_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), fd_si := ifelse(fd_si==0, i.fd_si,fd_si)]
avg_op_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), hm_si := ifelse(hm_si==0, i.hm_si,hm_si)]
avg_op_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), hw_si := ifelse(hw_si==0, i.hw_si,hw_si)]
avg_op_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), lt_si := ifelse(lt_si==0, i.lt_si,lt_si)]  
avg_op_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), lw_si := ifelse(lw_si==0, i.lw_si,lw_si)]
avg_op_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), pa_si := ifelse(pa_si==0, i.pa_si,pa_si)]
avg_op_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), pl_si := ifelse(pl_si==0, i.pl_si,pl_si)]
avg_op_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), pw_si := ifelse(pw_si==0, i.pw_si,pw_si)]
avg_op_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), py_si := ifelse(py_si==0, i.py_si,py_si)]
avg_op_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), sb_si := ifelse(sb_si==0, i.sb_si,sb_si)]
avg_op_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), se_si := ifelse(se_si==0, i.se_si,se_si)]
avg_op_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), ss_si := ifelse(ss_si==0, i.ss_si,ss_si)]
avg_op_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), sw_si := ifelse(sw_si==0, i.sw_si,sw_si)]
avg_op_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), sx_si := ifelse(sx_si==0, i.sx_si,sx_si)]
avg_op_data[avg_BEC_data, on=c("bec_zone","bec_subzone"), yc_si := ifelse(yc_si==0, i.yc_si,yc_si)]

# add src

avg_op_data$si_src <- 'PSPL'


# pre delete table
if(dbExistsTable(con,'pspl_op_site_index')) {
  db_drop_table(con,'pspl_op_site_index')
}

file_name <- 'D:/data/data_projects/PSPL_2021/pspl_op_site_index.csv'
fwrite(avg_op_data, file_name, col.names=TRUE, row.names=FALSE, quote = FALSE, sep=",")


dbWriteTable(con,'pspl_op_site_index',avg_op_data,row.names = FALSE)


```


```{r cleanUp}


if(dbExistsTable(con,'pspl_fid_site_index_pre_convert')) {
  db_drop_table(con,'pspl_fid_site_index_pre_convert')
}

if(dbExistsTable(con,'pspl_op_site_index_pre_convert')) {
  db_drop_table(con,'pspl_op_site_index_pre_convert')
}

if(dbExistsTable(con,'pspl_bec_site_index_pre_convert')) {
  db_drop_table(con,'pspl_bec_site_index_pre_convert')
}

dbDisconnect(con)

```



End: `r format(Sys.time(),"%c")`