---
title: "Read Convresion Coefficients"
author: "dwaddell"
date: '2022-05-19'
output: md_document
---


Table of site idnex conversion coefficients.  
Taken from Sindex by Ken Pollson  


s1 = species that has a missing site index value  
s2 = acceptable species site index that can be used to convert from  
b0 = intercept  
b1 = slope   
flag = extra conversion field


```{r}

library(kableExtra)

fname <- paste0(substr(getwd(),1,1),':/Data/GitManagedProjects/FAIB_PSPL/04_site_index_conversions/conversion_equations.txt')

coeff <- data.table::fread(fname,sep=',')


kable(coeff,format="markdown",caption = 'Species Site Index Conversion Coefficients') %>%
kable_styling(bootstrap_options = c("striped"),full_width=F,font_size=13,position = 'left')



```

Table 1.  Conversion Coefficients.

Note that a flag is used under certain conditions.  
This follows the C code implimetation.  

In general C/I indicates coast interior and is used for Cedare, Hemlock and Douglas Fir.  

SS, SW are used to indicate coast / interior and differentiate between Sitka spruce, Englemann spruce and White spruce when refernencing Sx as a hybrid. 


```{r eval=FALSE}


# add attribution to match how C handled things  
# coast interior indicator
  
  dt$c_i <- case_when(
    dt$bec_zone == 'CWH' ~ 'C',
    dt$bec_zone == 'CDF' ~ 'C',
    dt$bec_zone == 'MH' ~ 'C',
    TRUE ~ 'I'
  )
  
# Original code uses indicator for Spruce depending on BEC
  
  dt$se_ss_sw <- case_when(
    dt$c_i == 'C' ~ 'SS',
    dt$c_i == 'I' & dt$bec_zone == 'ESSF' ~ 'SE',
    TRUE ~ 'SW'
  )
  

