---
title: "PSPL Site Index Conversion"
output: html_document
---


# PSPL Method 2022   

## Version testing

2022.dec.13

Version 3.0


## feature_id processing 


Requires the following tables:

- pspl_site_index_mean_op



Start: `r format(Sys.time(),"%c")`

```{r setup, echo=FALSE,message=FALSE,warning=FALSE}

year <- '2022'

library(RPostgreSQL)
library(tidyverse)
library(data.table)
library(ggplot2)
library(kableExtra)

# set up for schema and user
schema <- 'msyt_2022'
opt <- paste0("-c search_path=",schema)
user_name <- 'results'
database <- 'msyt'
con <- dbConnect('PostgreSQL',dbname='msyt',user=user_name,options=opt)


#load the R code for site index conversions


si_convert <- paste0(getwd(),'/site_index_conversion_equations_v3.r')

source(si_convert, local = knitr::knit_global())

kablep <- function (x) {
  kable(x) %>%
  kable_styling(bootstrap_options = c("striped"),full_width=F,font_size=13,position = 'left')
}


```


```{r define_functions, echo=FALSE,message=FALSE,warning=FALSE}


# function to derive where species do no have a site index
assign_missing <- function(d){
  
  
  setDF(d)
  
  # set NA to 0 
  d[is.na(d)] <- 0
  
  # convert 3 char species to 2 char
  # Cwc,Fdc,Hwc
  d$species <- gsub('Cwc','Cw',d$species)
  d$species <- gsub('Cwi','Cw',d$species)
  d$species <- gsub('Fdc','Fd',d$species)
  d$species <- gsub('Fdi','Fd',d$species)
  d$species <- gsub('Hwc','Hw',d$species)
  d$species <- gsub('Hwi','Hw',d$species)
  
  d$missing <- ''
  
  d$missing <- case_when(
    grepl('At',d$species) & d$at_si == 0 ~ 'At',
    TRUE ~ ''
  )
  
  sp <- c('Ba','Bg','Bl','Cw','Dr','Ep','Fd','Hm','Hw','Lt','Lw','Pa','Pl','Pw','Py','Sb','Se','Ss','Sw','Yc')
  
  # use the at_si column as reference
  n <- which(colnames(d)=='at_si')
  #n <- 3
  for (s in sp) {
    
    n <- n + 1
    d$missing <- case_when(
      grepl(s,d$species) & d[,n] == 0 ~ paste0(d$missing,':',s),
      TRUE ~ paste0(d$missing,'')
    )
    
  }
  
  return(d)
  
}



call_si_conversion <- function(inp,tag) {
  
	# cast to table
  dt <- setDT(inp)
  
  # ************************************
  # Fix Sx: Sw, Se and Ss from Sx based on BEC
  
  if(tag == 0) {
  
    inp$sw_si <- case_when(
      !inp$bec_zone %in% c('CDF','CWH','MH') & inp$bec_zone != 'ESSF' & inp$sx_si != 0 ~ inp$sx_si,
      TRUE ~ inp$sw_si
    )
  
    inp$se_si <- case_when(
      inp$bec_zone == 'ESSF' & inp$sx_si != 0 ~ inp$sx_si,
      TRUE ~ inp$se_si
    )
  
    inp$ss_si <- case_when(
      inp$bec_zone %in% c('CDF','CWH','MH') & inp$sx_si != 0 ~ inp$sx_si,
      TRUE ~ inp$ss_si
    )
  }

	
	#### Spruce
	# ********************************************************************
	# Spruce   Se Sw Sx all interchange
	# set sw = sx
	dt$sw_si[which(dt$sw_si==0)] <- convert_sw_from_sx(dt[which(dt$sw_si==0)]) 
	
	# set sw = se 
	dt$sw_si[which(dt$sw_si==0)] <- convert_sw_from_se(dt[which(dt$sw_si==0)]) 
	
	# set se = sw
	dt$se_si[which(dt$se_si==0)] <- convert_se_from_sw(dt[which(dt$se_si==0)])
	
	# set ss = sx
	dt$ss_si[which(dt$ss_si==0)] <- convert_ss_from_sx(dt[which(dt$ss_si==0)]) 
	
	#### Spruce
	# **************************************************************************
	
	
	# sp <- At 'Ba','Bg','Bl','Cw','Dr','Ep','Fd','Hm','Hw','Lt','Lw','Pa','Pl','Pw','Py','Sb','Se','Ss','Sw','Yc')
	
	# At  
	dt$at_si[which(dt$at_si==0 & grepl('At',dt$missing))] <- convert_at_si(dt[which(dt$at_si==0 & grepl('At',dt$missing))])
	
	# Ba 
	dt$ba_si[which(dt$ba_si==0 & grepl('Ba',dt$missing))] <- convert_ba_si(dt[which(dt$ba_si==0 & grepl('Ba',dt$missing))])
	
	
	# Bl
	dt$bl_si[which(dt$bl_si==0 & grepl('Bl',dt$missing))] <- convert_bl_si(dt[which(dt$bl_si==0 & grepl('Bl',dt$missing))])
	
	# Cwc
	dt$cw_si[which(dt$cw_si==0 & grepl('Cw',dt$missing))] <- convert_cw_si(dt[which(dt$cw_si==0 & grepl('Cw',dt$missing))])
	
	# Fdc
	dt$fd_si[which(dt$fd_si==0 & grepl('Fd',dt$missing) & dt$bec_zone %in% c('CDF','CWH','MH') )] <- convert_fdc_si(dt[which(dt$fd_si==0 & grepl('Fd',dt$missing) & dt$bec_zone %in% c('CDF','CWH','MH') )])
	
	# Fdi
	dt$fd_si[which(dt$fd_si==0 & grepl('Fd',dt$missing) & !dt$bec_zone %in% c('CDF','CWH','MH') )] <- convert_fdi_si(dt[which(dt$fd_si==0 & grepl('Fd',dt$missing) & !dt$bec_zone %in% c('CDF','CWH','MH') )])
	
	# hw coast
	dt$hw_si[which(dt$hw_si==0 & grepl('Hw',dt$missing) & dt$bec_zone %in% c('CDF','CWH','MH') )] <- convert_hwc_si(dt[which(dt$hw_si==0 & grepl('Hw',dt$missing) & dt$bec_zone %in% c('CDF','CWH','MH') )])
	
	# hw interior
	dt$hw_si[which(dt$hw_si==0 & grepl('Hw',dt$missing) & !dt$bec_zone %in% c('CDF','CWH','MH') )] <- convert_hwi_si(dt[which(dt$hw_si==0 & grepl('Hw',dt$missing) & !dt$bec_zone %in% c('CDF','CWH','MH') )])
	
	
	# Lw
	dt$lw_si[which(dt$lw_si==0)] <- convert_lw_si(dt[which(dt$lw_si==0)])
	
	# Pl
	dt$pl_si[which(dt$pl_si==0)] <- convert_pl_si(dt[which(dt$pl_si==0)])
	
	# Sb
	dt$sb_si[which(dt$sb_si==0)] <- convert_sb_si(dt[which(dt$sb_si==0)])
	
	# Ss (coastal)
	dt$ss_si[which(dt$ss_si==0)] <- convert_ss_si(dt[which(dt$ss_si==0)])
	
	# Sw
	dt$sw_si[which(dt$sw_si==0)] <- convert_sw_si(dt[which(dt$sw_si==0)])
	
	# Pw
	dt$pw_si[which(dt$pw_si==0 & grepl('Pw',dt$missing))] <- convert_pw(dt[which(dt$pw_si==0 & grepl('Pw',dt$missing))])
	
	# Pa
	dt$pa_si[which(dt$pa_si==0 & grepl('Pa',dt$missing))] <- convert_pa(dt[which(dt$pa_si==0 & grepl('Pa',dt$missing))])
	
	# Py
	dt$py_si[which(dt$py_si==0 & grepl('Py',dt$missing))] <- convert_py(dt[which(dt$py_si==0 & grepl('Py',dt$missing))]) 
	
	
	# Dr Coast/Interior
	dt$dr_si[which(dt$dr_si==0 & grepl('Dr',dt$missing))] <- convert_dr(dt[which(dt$dr_si==0 & grepl('Dr',dt$missing))])  
	
	# 1-1
	
	# Bg 1-1
	dt$bg_si[which(dt$bg_si==0 & grepl('Bg',dt$missing))] <- convert_bg(dt[which(dt$bg_si==0 & grepl('Bg',dt$missing))])
	dt$bl_si[which(dt$bl_si==0 & grepl('Bl',dt$missing))] <- convert_bl(dt[which(dt$bl_si==0 & grepl('Bl',dt$missing))])
	dt$ba_si[which(dt$ba_si==0 & grepl('Ba',dt$missing))] <- convert_ba(dt[which(dt$ba_si==0 & grepl('Ba',dt$missing))])
	
	# Lw Lt 
	dt$lt_si[which(dt$lt_si==0 & grepl('Lt',dt$missing))] <- convert_lt_from_lw(dt[which(dt$lt_si==0 & grepl('Lt',dt$missing))])
	
	# ********************************************************************
	# Spruce   Se Sw Sx all interchange
	# set sw = sx
	
	dt$sw_si[which(dt$sw_si==0)] <- convert_sw_from_sx(dt[which(dt$sw_si==0)]) 
	
	# set sw = se 
	dt$sw_si[which(dt$sw_si==0)] <- convert_sw_from_se(dt[which(dt$sw_si==0)]) 
	
	# set se = sw
	dt$se_si[which(dt$se_si==0)] <- convert_se_from_sw(dt[which(dt$se_si==0)])
	
	# set ss = sx
	dt$ss_si[which(dt$ss_si==0)] <- convert_ss_from_sx(dt[which(dt$ss_si==0)]) 
	
	# can not do this because opening id can be negative
  #dt[dt <0 ] <- 0.0
  
  dt$at_si[dt$at_si < 0 ] <- 0.0
  dt$ba_si[dt$ba_si < 0 ] <- 0.0
  dt$bg_si[dt$bg_si < 0 ] <- 0.0
  dt$bl_si[dt$bl_si < 0 ] <- 0.0
  dt$cw_si[dt$cw_si < 0 ] <- 0.0
  dt$dr_si[dt$dr_si < 0 ] <- 0.0
  dt$ep_si[dt$ep_si < 0 ] <- 0.0
  dt$fd_si[dt$fd_si < 0 ] <- 0.0
  dt$hm_si[dt$hm_si < 0 ] <- 0.0
  dt$hw_si[dt$hw_si < 0 ] <- 0.0
  dt$lt_si[dt$lt_si < 0 ] <- 0.0
  dt$lw_si[dt$lw_si < 0 ] <- 0.0
  dt$pa_si[dt$pa_si < 0 ] <- 0.0
  dt$pl_si[dt$pl_si < 0 ] <- 0.0
  dt$pw_si[dt$pw_si < 0 ] <- 0.0
  dt$py_si[dt$py_si < 0 ] <- 0.0
  dt$sb_si[dt$sb_si < 0 ] <- 0.0
  dt$se_si[dt$se_si < 0 ] <- 0.0
  dt$ss_si[dt$ss_si < 0 ] <- 0.0
  dt$sw_si[dt$sw_si < 0 ] <- 0.0
  dt$sx_si[dt$sx_si < 0 ] <- 0.0
  dt$yc_si[dt$yc_si < 0 ] <- 0.0
  

  
  #convert to numeric 1
  dt <- dt %>% mutate_if(is.numeric, round, digits=1)
	
	return(dt)
}



bec_conversions <- function(inp){
setDT(inp)

inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), at_si := ifelse(at_si==0, i.at_si,at_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), ba_si := ifelse(ba_si==0, i.ba_si,ba_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), bg_si := ifelse(bg_si==0, i.bg_si,bg_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), bl_si := ifelse(bl_si==0, i.bl_si,bl_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), cw_si := ifelse(cw_si==0, i.cw_si,cw_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), dr_si := ifelse(dr_si==0, i.dr_si,dr_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), ep_si := ifelse(ep_si==0, i.ep_si,ep_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), fd_si := ifelse(fd_si==0, i.fd_si,fd_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), hm_si := ifelse(hm_si==0, i.hm_si,hm_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), hw_si := ifelse(hw_si==0, i.hw_si,hw_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), lt_si := ifelse(lt_si==0, i.lt_si,lt_si)]  
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), lw_si := ifelse(lw_si==0, i.lw_si,lw_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), pa_si := ifelse(pa_si==0, i.pa_si,pa_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), pl_si := ifelse(pl_si==0, i.pl_si,pl_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), pw_si := ifelse(pw_si==0, i.pw_si,pw_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), py_si := ifelse(py_si==0, i.py_si,py_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), sb_si := ifelse(sb_si==0, i.sb_si,sb_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), se_si := ifelse(se_si==0, i.se_si,se_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), ss_si := ifelse(ss_si==0, i.ss_si,ss_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), sw_si := ifelse(sw_si==0, i.sw_si,sw_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), sx_si := ifelse(sx_si==0, i.sx_si,sx_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), yc_si := ifelse(yc_si==0, i.yc_si,yc_si)]

return(inp)
}





```

### run SI conversion 


- run SI conversion on BEC based si 

This has to be run first as any missing values in fid or opening use this table

```{r bec_si_convert, echo=FALSE,message=FALSE,warning=FALSE}

# read avg_BEC_data: table = psql_bec_site_index_pre_convert
q1 <- paste0('select *  from msyt_',year,'.pspl_site_index_mean_bec')
avg_BEC_data <- dbGetQuery(con,q1)

# get species that are assigned from RESULTS
# can be a combination of Planted and Natural
species <- dbGetQuery(con,"select bec_zone,bec_subzone,array_to_string(species,',') as species from species_list_bec_agg")

# join species to BEC
avg_BEC_data <- left_join(avg_BEC_data,species)



df_base <- avg_BEC_data

#df <- avg_BEC_data

df_base$id <- 1:nrow(df_base)

df_base <- assign_missing(df_base)

# split into those with missing and those without
df <- df_base %>% subset(missing != '') 
df_base <- df_base %>% subset(!id %in% df$id)
  
 

df <- call_si_conversion(df,0)


df <- assign_missing(df)


#x1 <- df %>% subset(missing != '')

# Force balsam BA Bg swap
# Lw Lt swap

#df$missing <- ':Ba:Bg:Bl:Lt'
#df <- call_si_conversion(df)

# back together
avg_BEC_data <- rbind(df_base,df)
#avg_BEC_data$missing <- ':Ba:Bg:Bl:Lt'
#avg_BEC_data <- call_si_conversion(avg_BEC_data)
#avg_BEC_data$missing <- ''

#x <- assign_missing(avg_BEC_data)
#x <- x %>% subset(missing != '')
# write the data
#file_name <- paste0(substr(getwd(),1,1),':/data/data_projects/AR',year,'/PSPL/si_data/pspl_site_index_bec.csv')
#fwrite(avg_BEC_data, file_name, col.names=TRUE, row.names=FALSE, quote = FALSE, sep=",")


#tbl_name <- paste0('pspl_site_index_bec')


# pre delete table
#if(dbExistsTable(con,tbl_name)) {
#  dbRemoveTable(con,tbl_name)
#}


# write to table
#dbWriteTable(con,tbl_name,avg_BEC_data,row.names = FALSE)


```



### Site Index Conversions

  

mean value data

`r format(Sys.time(),"%c")`

```{r  si_convert_init,echo=FALSE,message=FALSE,warning=FALSE}


# read avg_op_data: table = pspl_site_index_mean_op
# this is the mean value feature_id data

#q1 <- paste0('select *  from msyt_',year,'.pspl_site_index_mean_op')
q1 <- paste0('select *  from msyt_',year,'.pspl_site_index_mean_fid')


si_data <- dbGetQuery(con,q1)


#species <- dbGetQuery(con,"select opening_id,array_to_string(species,',') as species ,b.bec_zone,b.bec_subzone from species_list_op a left join veg_bec_op b using(opening_id)")
#species <- dbGetQuery(con,"select feature_id,array_to_string(species,',') as species ,bec_zone,bec_subzone from species_list_current_fid")
species <- dbGetQuery(con,"select feature_id,array_to_string(species,',') as species ,bec_zone,bec_subzone from species_list_future_fid")



#si_data <- left_join(species,si_data,by='opening_id')
si_data <- left_join(species,si_data,by='feature_id')

#avg_data <- avg_data %>% subset(!is.na(species))

# required to assing the missing
# si conversion only applis where there are missing values
si_data <- assign_missing(si_data)






#avg_data <- avg_data %>% subset(missing != '')  # %>% subset(bec_zone != 'IMA')

si_data <- call_si_conversion(si_data,0)

si_data <- assign_missing(si_data)

c1 <- count(si_data,missing) %>% arrange(desc(n))
c1 <- head(c1,4)




kablep(c1)




```

Table 1. Initial missing species site index


`r format(Sys.time(),"%c")`

```{r si_convert_step2,eval=TRUE,echo=FALSE,message=FALSE,warning=FALSE}

si_data <- bec_conversions(si_data)
  
si_data <- assign_missing(si_data)

c1 <- count(si_data,missing) %>% arrange(desc(n))
kablep(c1)

```

Table 2. After BEC substitutions

`r format(Sys.time(),"%c")`

```{r si_convert_step3,eval=TRUE,echo=FALSE,message=FALSE,warning=FALSE}

# run the conversions again to fill in the final missing site index values
si_data <- call_si_conversion(si_data,1)

si_data <- assign_missing(si_data)

c1 <- count(si_data,missing) %>% arrange(desc(n))
 
kablep(c1)

```

Table 3. Final missing

```{r write,eval=FALSE,echo=FALSE,message=FALSE,warning=FALSE}


# add src

avg_fid_data$si_src <- 'PSPL'

# write the data
file_name <- paste0(substr(getwd(),1,1),':/data/data_projects/AR',year,'/PSPL/si_data/pspl_site_index_fid.csv')
#fwrite(avg_fid_data, file_name, col.names=TRUE, row.names=FALSE, quote = FALSE, sep=",")


tbl_name <- paste0('pspl_site_index_fid')

# pre delete table
if(dbExistsTable(con,tbl_name)) {
  dbRemoveTable(con,tbl_name)
}

# write to table

dbWriteTable(con,tbl_name,avg_fid_data,row.names = FALSE)

```







```{r dump_table, echo=FALSE,message=FALSE,warning=FALSE}

pg_dump <- function(t_name,folder){
  
  # -O required to negate ownership
  
  f_out <- paste0(folder,'msyt_',year,'_',t_name,'.sql')
  tbl <- paste0('msyt_',year,'.',t_name)
  
  q1 <- paste0("-d ",
               database,
               " -O",
                " -t ",
                tbl,
               " -f ",
               f_out )
  
  system2("pg_dump",args=q1,stderr=TRUE,wait=TRUE)
  #print(q1)
}

```


```{r dump,eval=FALSE,echo=FALSE,message=FALSE,warning=FALSE}

folder <- paste0(substr(getwd(),1,1),':/data/data_projects/AR',year,'/pg_dump/')

table <- 'pspl_site_index_bec'
pg_dump(table,folder)

table <- 'pspl_site_index_fid'
pg_dump(table,folder)

table <- 'pspl_site_index_op'
pg_dump(table,folder)




# drop the foreign table

#q1 <- paste0('drop foreign table load_',year,'.veg_comp_lyr_r1_poly')
#dbExecute(con,q1)

```




```{r discon, echo=FALSE,message=FALSE,warning=FALSE}

z <- dbDisconnect(con)

```



End: `r format(Sys.time(),"%c")`