---
title: "PSPL Site Index Conversion"
output: md_document
---


# PSPL Method 2022   

## Version 3.1

2023.feb.17

Version 3.1

Process Order:  

- load features with species from MSYT process
- Sx conversion
- First conversion SIndex coefficients
- BEC bases substitutions




## feature_id processing 


Requires the following tables:

- site_index_mean_fid
- site_index_mean_bec



Start: `r format(Sys.time(),"%c")`

```{r setup, echo=FALSE,message=FALSE,warning=FALSE}

year <- '2022'

library(RPostgreSQL)
library(tidyverse)
library(data.table)
library(ggplot2)
library(kableExtra)

# set up for schema and user
schema <- 'msyt_2022'
opt <- paste0("-c search_path=",schema)
user_name <- 'results'
database <- 'msyt'
con <- dbConnect('PostgreSQL',dbname='msyt',user=user_name,options=opt)


#load the R code for site index conversions
si_convert <- paste0(getwd(),'/site_index_conversion_equations_v3.r')

source(si_convert, local = knitr::knit_global())

#kablep <- function (x) {
#  kable(x) %>%
#  kable_styling(bootstrap_options = c("striped"),full_width=F,font_size=13,position = 'left')
#}


```


```{r define_functions, echo=FALSE,message=FALSE,warning=FALSE}


# function to derive where species do no have a site index
assign_missing <- function(d){
  
  setDF(d)
  
  # set NA to 0 
  d[is.na(d)] <- 0
  
  # convert 3 char species to 2 char
  # Cwc,Fdc,Hwc
  d$species <- gsub('Cwc','Cw',d$species)
  d$species <- gsub('Cwi','Cw',d$species)
  d$species <- gsub('Fdc','Fd',d$species)
  d$species <- gsub('Fdi','Fd',d$species)
  d$species <- gsub('Hwc','Hw',d$species)
  d$species <- gsub('Hwi','Hw',d$species)
  
  d$missing <- ''
  
  d$missing <- case_when(
    grepl('At',d$species) & d$at_si == 0 ~ 'At',
    TRUE ~ ''
  )
  
  sp <- c('Ba','Bg','Bl','Cw','Dr','Ep','Fd','Hm','Hw','Lt','Lw','Pa','Pl','Pw','Py','Sb','Se','Ss','Sw','Yc')
  
  # use the at_si column as reference
  n <- which(colnames(d)=='at_si')
  #n <- 3
  for (s in sp) {
    
    n <- n + 1
    d$missing <- case_when(
      grepl(s,d$species) & d[,n] == 0 ~ paste0(d$missing,':',s),
      TRUE ~ paste0(d$missing,'')
    )
    
  }
  
  return(d)
  
}

# Sw, Se, Ss from Sx conversions based on BEC
#  assume that spruce is equal 
spruce_conversion <- function(dt){
  # cast to data.table
  setDT(dt)
  
  # ************************************
  # Fix Sx: Sw, Se and Ss from Sx based on BEC
  
    dt$sw_si <- case_when(
      !dt$bec_zone %in% c('CDF','CWH','MH') & dt$bec_zone != 'ESSF' & dt$sx_si != 0 ~ dt$sx_si,
      TRUE ~ dt$sw_si
    )
  
    dt$se_si <- case_when(
      dt$bec_zone == 'ESSF' & dt$sx_si != 0 ~ dt$sx_si,
      TRUE ~ dt$se_si
    )
  
    dt$ss_si <- case_when(
      dt$bec_zone %in% c('CDF','CWH','MH') & dt$sx_si != 0 ~ dt$sx_si,
      TRUE ~ dt$ss_si
    )
    
    #### Spruce  swap Se Sw Sx
	# ********************************************************************
	# Spruce   Se Sw Sx all interchange
	# set sw = sx
	dt$sw_si[which(dt$sw_si==0)] <- convert_sw_from_sx(dt[which(dt$sw_si==0)]) 
	
	# set sw = se 
	dt$sw_si[which(dt$sw_si==0)] <- convert_sw_from_se(dt[which(dt$sw_si==0)]) 
	
	# set se = sw
	dt$se_si[which(dt$se_si==0)] <- convert_se_from_sw(dt[which(dt$se_si==0)])
	
	# set ss = sx
	dt$ss_si[which(dt$ss_si==0)] <- convert_ss_from_sx(dt[which(dt$ss_si==0)]) 
	
	#### Spruce
	# **************************************************************************
    
  return(dt)
  
  
}



base_si_conversion <- function(dt) {
  
	# cast to data.table
  setDT(dt)
	
	# At  
	dt$at_si[which(dt$at_si==0 & grepl('At',dt$missing))] <- convert_at_si(dt[which(dt$at_si==0 & grepl('At',dt$missing))])
	
	# Ba 
	dt$ba_si[which(dt$ba_si==0 & grepl('Ba',dt$missing))] <- convert_ba_si(dt[which(dt$ba_si==0 & grepl('Ba',dt$missing))])
	
	
	# Bl
	dt$bl_si[which(dt$bl_si==0 & grepl('Bl',dt$missing))] <- convert_bl_si(dt[which(dt$bl_si==0 & grepl('Bl',dt$missing))])
	
	# Cwc
	dt$cw_si[which(dt$cw_si==0 & grepl('Cw',dt$missing))] <- convert_cw_si(dt[which(dt$cw_si==0 & grepl('Cw',dt$missing))])
	
	# Fdc
	dt$fd_si[which(dt$fd_si==0 & grepl('Fd',dt$missing) & dt$bec_zone %in% c('CDF','CWH','MH') )] <- convert_fdc_si(dt[which(dt$fd_si==0 & grepl('Fd',dt$missing) & dt$bec_zone %in% c('CDF','CWH','MH') )])
	
	# Fdi
	dt$fd_si[which(dt$fd_si==0 & grepl('Fd',dt$missing) & !dt$bec_zone %in% c('CDF','CWH','MH') )] <- convert_fdi_si(dt[which(dt$fd_si==0 & grepl('Fd',dt$missing) & !dt$bec_zone %in% c('CDF','CWH','MH') )])
	
	# hw coast
	dt$hw_si[which(dt$hw_si==0 & grepl('Hw',dt$missing) & dt$bec_zone %in% c('CDF','CWH','MH') )] <- convert_hwc_si(dt[which(dt$hw_si==0 & grepl('Hw',dt$missing) & dt$bec_zone %in% c('CDF','CWH','MH') )])
	
	# hw interior
	dt$hw_si[which(dt$hw_si==0 & grepl('Hw',dt$missing) & !dt$bec_zone %in% c('CDF','CWH','MH') )] <- convert_hwi_si(dt[which(dt$hw_si==0 & grepl('Hw',dt$missing) & !dt$bec_zone %in% c('CDF','CWH','MH') )])
	
	
	# Lw
	dt$lw_si[which(dt$lw_si==0 & grepl('Lw',dt$missing))] <- convert_lw_si(dt[which(dt$lw_si==0 & grepl('Lw',dt$missing))])
	
	# Pl
	dt$pl_si[which(dt$pl_si==0 & grepl('Pl',dt$missing))] <- convert_pl_si(dt[which(dt$pl_si==0 & grepl('Pl',dt$missing))])
	
	# Sb
	dt$sb_si[which(dt$sb_si==0 & grepl('Sb',dt$missing))] <- convert_sb_si(dt[which(dt$sb_si==0 & grepl('Sb',dt$missing))])
	
	# Ss (coastal)
	dt$ss_si[which(dt$ss_si==0 & grepl('Ss',dt$missing))] <- convert_ss_si(dt[which(dt$ss_si==0 & grepl('Ss',dt$missing))])
	
	# Sw
	dt$sw_si[which(dt$sw_si==0 & grepl('Sw',dt$missing))] <- convert_sw_si(dt[which(dt$sw_si==0 & grepl('Sw',dt$missing))])
	
	# Pw
	dt$pw_si[which(dt$pw_si==0 & grepl('Pw',dt$missing))] <- convert_pw(dt[which(dt$pw_si==0 & grepl('Pw',dt$missing))])
	
	# Pa
	dt$pa_si[which(dt$pa_si==0 & grepl('Pa',dt$missing))] <- convert_pa(dt[which(dt$pa_si==0 & grepl('Pa',dt$missing))])
	
	# Py
	dt$py_si[which(dt$py_si==0 & grepl('Py',dt$missing))] <- convert_py(dt[which(dt$py_si==0 & grepl('Py',dt$missing))]) 
	
	
	# Dr Coast/Interior
	dt$dr_si[which(dt$dr_si==0 & grepl('Dr',dt$missing))] <- convert_dr(dt[which(dt$dr_si==0 & grepl('Dr',dt$missing))])  
	
	# 1-1
	
	# Bg 1-1
	dt$bg_si[which(dt$bg_si==0 & grepl('Bg',dt$missing))] <- convert_bg(dt[which(dt$bg_si==0 & grepl('Bg',dt$missing))])
	dt$bl_si[which(dt$bl_si==0 & grepl('Bl',dt$missing))] <- convert_bl(dt[which(dt$bl_si==0 & grepl('Bl',dt$missing))])
	dt$ba_si[which(dt$ba_si==0 & grepl('Ba',dt$missing))] <- convert_ba(dt[which(dt$ba_si==0 & grepl('Ba',dt$missing))])
	
	# Lw Lt 
	dt$lt_si[which(dt$lt_si==0 & grepl('Lt',dt$missing))] <- convert_lt_from_lw(dt[which(dt$lt_si==0 & grepl('Lt',dt$missing))])
	
	# ********************************************************************
	# Spruce   Se Sw Sx all interchange
	# set sw = sx
	
	#dt$sw_si[which(dt$sw_si==0)] <- convert_sw_from_sx(dt[which(dt$sw_si==0)]) 
	
	# set sw = se 
	#dt$sw_si[which(dt$sw_si==0)] <- convert_sw_from_se(dt[which(dt$sw_si==0)]) 
	
	# set se = sw
	#dt$se_si[which(dt$se_si==0)] <- convert_se_from_sw(dt[which(dt$se_si==0)])
	
	# set ss = sx
	#dt$ss_si[which(dt$ss_si==0)] <- convert_ss_from_sx(dt[which(dt$ss_si==0)]) 
	
	# can not do this because opening id can be negative
  #dt[dt <0 ] <- 0.0
  
  dt$at_si[dt$at_si < 0 ] <- 0.0
  dt$ba_si[dt$ba_si < 0 ] <- 0.0
  dt$bg_si[dt$bg_si < 0 ] <- 0.0
  dt$bl_si[dt$bl_si < 0 ] <- 0.0
  dt$cw_si[dt$cw_si < 0 ] <- 0.0
  dt$dr_si[dt$dr_si < 0 ] <- 0.0
  dt$ep_si[dt$ep_si < 0 ] <- 0.0
  dt$fd_si[dt$fd_si < 0 ] <- 0.0
  dt$hm_si[dt$hm_si < 0 ] <- 0.0
  dt$hw_si[dt$hw_si < 0 ] <- 0.0
  dt$lt_si[dt$lt_si < 0 ] <- 0.0
  dt$lw_si[dt$lw_si < 0 ] <- 0.0
  dt$pa_si[dt$pa_si < 0 ] <- 0.0
  dt$pl_si[dt$pl_si < 0 ] <- 0.0
  dt$pw_si[dt$pw_si < 0 ] <- 0.0
  dt$py_si[dt$py_si < 0 ] <- 0.0
  dt$sb_si[dt$sb_si < 0 ] <- 0.0
  dt$se_si[dt$se_si < 0 ] <- 0.0
  dt$ss_si[dt$ss_si < 0 ] <- 0.0
  dt$sw_si[dt$sw_si < 0 ] <- 0.0
  dt$sx_si[dt$sx_si < 0 ] <- 0.0
  dt$yc_si[dt$yc_si < 0 ] <- 0.0
  

  
  #convert to numeric 1
  dt <- dt %>% mutate_if(is.numeric, round, digits=1)
	
	return(dt)
}




base_si_conversion_pass2 <- function(dt) {
  
	# cast to data.table
  setDT(dt)
	
	# At  
	dt$at_si[which(dt$at_si==0 )] <- convert_at_si(dt[which(dt$at_si==0  )])
	
	# Ba 
	dt$ba_si[which(dt$ba_si==0 )] <- convert_ba_si(dt[which(dt$ba_si==0 )])
	
	
	# Bl
	dt$bl_si[which(dt$bl_si==0 )] <- convert_bl_si(dt[which(dt$bl_si==0 )])
	
	# Cwc
	dt$cw_si[which(dt$cw_si==0 )] <- convert_cw_si(dt[which(dt$cw_si==0 )])
	
	# Fdc
	dt$fd_si[which(dt$fd_si==0  & dt$bec_zone %in% c('CDF','CWH','MH') )] <- convert_fdc_si(dt[which(dt$fd_si==0  & dt$bec_zone %in% c('CDF','CWH','MH') )])
	
	# Fdi
	dt$fd_si[which(dt$fd_si==0  & !dt$bec_zone %in% c('CDF','CWH','MH') )] <- convert_fdi_si(dt[which(dt$fd_si==0  & !dt$bec_zone %in% c('CDF','CWH','MH') )])
	
	# hw coast
	dt$hw_si[which(dt$hw_si==0  & dt$bec_zone %in% c('CDF','CWH','MH') )] <- convert_hwc_si(dt[which(dt$hw_si==0 & dt$bec_zone %in% c('CDF','CWH','MH') )])
	
	# hw interior
	dt$hw_si[which(dt$hw_si==0  & !dt$bec_zone %in% c('CDF','CWH','MH') )] <- convert_hwi_si(dt[which(dt$hw_si==0 & !dt$bec_zone %in% c('CDF','CWH','MH') )])
	
	
	# Lw
	dt$lw_si[which(dt$lw_si==0)] <- convert_lw_si(dt[which(dt$lw_si==0 )])
	
	# Pl
	dt$pl_si[which(dt$pl_si==0 )] <- convert_pl_si(dt[which(dt$pl_si==0)])
	
	# Sb
	dt$sb_si[which(dt$sb_si==0 )] <- convert_sb_si(dt[which(dt$sb_si==0 )])
	
	# Ss (coastal)
	dt$ss_si[which(dt$ss_si==0 )] <- convert_ss_si(dt[which(dt$ss_si==0)])
	
	# Sw
	dt$sw_si[which(dt$sw_si==0)] <- convert_sw_si(dt[which(dt$sw_si==0 )])
	
	# Pw
	dt$pw_si[which(dt$pw_si==0 )] <- convert_pw(dt[which(dt$pw_si==0 )])
	
	# Pa
	dt$pa_si[which(dt$pa_si==0 )] <- convert_pa(dt[which(dt$pa_si==0 )])
	
	# Py
	dt$py_si[which(dt$py_si==0 )] <- convert_py(dt[which(dt$py_si==0 )]) 
	
	
	# Dr Coast/Interior
	dt$dr_si[which(dt$dr_si==0)] <- convert_dr(dt[which(dt$dr_si==0 )])  
	
	# 1-1
	
	# Bg 1-1
	dt$bg_si[which(dt$bg_si==0 )] <- convert_bg(dt[which(dt$bg_si==0 )])
	dt$bl_si[which(dt$bl_si==0 )] <- convert_bl(dt[which(dt$bl_si==0 )])
	dt$ba_si[which(dt$ba_si==0 )] <- convert_ba(dt[which(dt$ba_si==0 )])
	
	# Lw Lt 
	dt$lt_si[which(dt$lt_si==0 )] <- convert_lt_from_lw(dt[which(dt$lt_si==0 )])
	
	# ********************************************************************
	# Spruce   Se Sw Sx all interchange
	# set sw = sx
	
	#dt$sw_si[which(dt$sw_si==0)] <- convert_sw_from_sx(dt[which(dt$sw_si==0)]) 
	
	# set sw = se 
	#dt$sw_si[which(dt$sw_si==0)] <- convert_sw_from_se(dt[which(dt$sw_si==0)]) 
	
	# set se = sw
	#dt$se_si[which(dt$se_si==0)] <- convert_se_from_sw(dt[which(dt$se_si==0)])
	
	# set ss = sx
	#dt$ss_si[which(dt$ss_si==0)] <- convert_ss_from_sx(dt[which(dt$ss_si==0)]) 
	
	# can not do this because opening id can be negative
  #dt[dt <0 ] <- 0.0
  
  dt$at_si[dt$at_si < 0 ] <- 0.0
  dt$ba_si[dt$ba_si < 0 ] <- 0.0
  dt$bg_si[dt$bg_si < 0 ] <- 0.0
  dt$bl_si[dt$bl_si < 0 ] <- 0.0
  dt$cw_si[dt$cw_si < 0 ] <- 0.0
  dt$dr_si[dt$dr_si < 0 ] <- 0.0
  dt$ep_si[dt$ep_si < 0 ] <- 0.0
  dt$fd_si[dt$fd_si < 0 ] <- 0.0
  dt$hm_si[dt$hm_si < 0 ] <- 0.0
  dt$hw_si[dt$hw_si < 0 ] <- 0.0
  dt$lt_si[dt$lt_si < 0 ] <- 0.0
  dt$lw_si[dt$lw_si < 0 ] <- 0.0
  dt$pa_si[dt$pa_si < 0 ] <- 0.0
  dt$pl_si[dt$pl_si < 0 ] <- 0.0
  dt$pw_si[dt$pw_si < 0 ] <- 0.0
  dt$py_si[dt$py_si < 0 ] <- 0.0
  dt$sb_si[dt$sb_si < 0 ] <- 0.0
  dt$se_si[dt$se_si < 0 ] <- 0.0
  dt$ss_si[dt$ss_si < 0 ] <- 0.0
  dt$sw_si[dt$sw_si < 0 ] <- 0.0
  dt$sx_si[dt$sx_si < 0 ] <- 0.0
  dt$yc_si[dt$yc_si < 0 ] <- 0.0
  

  
  #convert to numeric 1
  dt <- dt %>% mutate_if(is.numeric, round, digits=1)
	
	return(dt)
}


bec_conversions <- function(inp){
setDT(inp)

inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), at_si := ifelse(at_si==0, i.at_si,at_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), ba_si := ifelse(ba_si==0, i.ba_si,ba_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), bg_si := ifelse(bg_si==0, i.bg_si,bg_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), bl_si := ifelse(bl_si==0, i.bl_si,bl_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), cw_si := ifelse(cw_si==0, i.cw_si,cw_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), dr_si := ifelse(dr_si==0, i.dr_si,dr_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), ep_si := ifelse(ep_si==0, i.ep_si,ep_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), fd_si := ifelse(fd_si==0, i.fd_si,fd_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), hm_si := ifelse(hm_si==0, i.hm_si,hm_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), hw_si := ifelse(hw_si==0, i.hw_si,hw_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), lt_si := ifelse(lt_si==0, i.lt_si,lt_si)]  
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), lw_si := ifelse(lw_si==0, i.lw_si,lw_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), pa_si := ifelse(pa_si==0, i.pa_si,pa_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), pl_si := ifelse(pl_si==0, i.pl_si,pl_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), pw_si := ifelse(pw_si==0, i.pw_si,pw_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), py_si := ifelse(py_si==0, i.py_si,py_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), sb_si := ifelse(sb_si==0, i.sb_si,sb_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), se_si := ifelse(se_si==0, i.se_si,se_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), ss_si := ifelse(ss_si==0, i.ss_si,ss_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), sw_si := ifelse(sw_si==0, i.sw_si,sw_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), sx_si := ifelse(sx_si==0, i.sx_si,sx_si)]
inp[avg_BEC_data, on=c("bec_zone","bec_subzone"), yc_si := ifelse(yc_si==0, i.yc_si,yc_si)]

return(inp)
}





```

  

## Load mean value site inde data from PSPL 

`r format(Sys.time(),"%c")`



```{r  si_convert_init,echo=FALSE,message=FALSE,warning=FALSE}

# read data

# from PostgreSQL
# read the pre convert table of site index with species list
si_data <- dbGetQuery(con,'select * from site_index_pre_conv_fid')


# species in PostgreSQL is an array
# this reads into R as a string with braces
# get rid of braces
si_data$species <- gsub('\\{','',si_data$species)
si_data$species <- gsub('\\}','',si_data$species)


# all si values NA need to be zero
si_data[is.na(si_data)] <- 0



# required to assign the missing
# si conversion only applies where there are missing values
si_data <- assign_missing(si_data)

# assign sort label
si_data$src <- 'PSPL'

# total rows
n_tot <- nrow(si_data)


# split into those that have valid si and those that have si missing

# those that require fixing
fix_si <- si_data %>% subset(missing != '') 
# those that are good
si_data <- si_data %>% subset(!missing != '') 

c1 <- count(si_data,src)

c1$pct <- as.integer(c1$n/n_tot*100)
p1 <- c1$pct
c1 <- rbind(c1,data.frame('src' = 'Total','n' = n_tot,'pct' = ''))

kable(c1,format='markdown')


```

Table 1.  Base PSPL Missing Site Index values

Initially, the raw PSPL has site index values for all required species for `r p1`%.



# Spruce conversions

Change SX to Sw, Se Ss based on BEC.  


```{r echo=FALSE,message=FALSE,warning=FALSE}

fix_si$src <- 'Spruce Conversion'
fix_si <- spruce_conversion(fix_si)
fix_si <- assign_missing(fix_si)

# put those that are fixed back into base
si_data <- rbind(si_data,fix_si[fix_si$missing=='',])

# those that require fixing
fix_si <- fix_si %>% subset(missing != '') 

c1 <- count(si_data,src)

c1$pct <- as.integer(c1$n/n_tot*100)
p2 <- sum(c1$pct)
c1 <- rbind(c1,data.frame('src' = 'Total','n' = n_tot,'pct' = ''))

kable(c1,format='markdown')

```

Table 2. After SX substitutions

After substituting for Sx, the valid site index percentage has increased to `r p2`%.



# Base conversion

Using SIndex coefficients

```{r base_convert,echo=FALSE,message=FALSE,warning=FALSE}

fix_si$src <- 'SIndex Conversion(1)'
fix_si <- base_si_conversion(fix_si)
fix_si <- assign_missing(fix_si)

# put those that are fixed back into base
si_data <- rbind(si_data,fix_si[fix_si$missing=='',])

# those that still require fixing
fix_si <- fix_si %>% subset(missing != '') 

c1 <- count(si_data,src)

c1$pct <- as.integer(c1$n/n_tot*100)
p2 <- sum(c1$pct)


c1 <- rbind(c1,data.frame('src' = 'Total','n' = n_tot,'pct' = ''))

c1$ord<- case_when(
  c1$src == 'PSPL' ~ 1,
  c1$src == 'Spruce Conversion' ~ 2,
  c1$src == 'SIndex Conversion(1)' ~ 3,
  TRUE ~ 4
)

c1 <- c1 %>% arrange(ord)
c1 <- c1 %>% select(-ord)

kable(c1,format='markdown')



```

Table 3. After SIndex conversions where a species is mising a site index.

The valid site index percentage has increased to `r p2`%.


# BEC site index substitutions

Based on mean BEC site index values from PSPL

```{r si_convert_step2,eval=TRUE,echo=FALSE,message=FALSE,warning=FALSE}

# for those still missing species site index
# use the bec based averages

avg_BEC_data <- dbGetQuery(con,'select * from pspl_site_index_mean_bec')
avg_BEC_data[is.na(avg_BEC_data)] <- 0

species2 <- dbGetQuery(con,'select species ,bec_zone,bec_subzone from species_list_bec_agg')

# get rid of braces
species2$species <- gsub('\\{','',species2$species)
species2$species <- gsub('\\}','',species2$species)


avg_BEC_data <- left_join(avg_BEC_data,species2,by=c('bec_zone','bec_subzone'))

# do the spruce conversions to the BEC data
avg_BEC_data <- spruce_conversion(avg_BEC_data)

# apply the BEC conversions
fix_si <- bec_conversions(fix_si)
  
fix_si <- assign_missing(fix_si)



fix_si$src <- 'BEC Conversion'

# put the fixed back 
si_data <- rbind(si_data,fix_si[fix_si$missing == '',])

fix_si <- fix_si %>% subset(missing != '')

c1 <- count(si_data,src)

c1$pct <- as.integer(c1$n/n_tot*100)
p2 <- sum(c1$pct)


c1 <- rbind(c1,data.frame('src' = 'Total','n' = n_tot,'pct' = ''))

c1$ord<- case_when(
  c1$src == 'PSPL' ~ 1,
  c1$src == 'Spruce Conversion' ~ 2,
  c1$src == 'SIndex Conversion(1)' ~ 3,
  c1$src == 'BEC Conversion' ~ 4,
  TRUE ~ 5
)

c1 <- c1 %>% arrange(ord)
c1 <- c1 %>% select(-ord)

kable(c1,format='markdown')

```

Table 4. After BEC substitutions. 

The valid site index percentage has increased to `r p2`%.

## Still missing


```{r echo=FALSE,message=FALSE,warning=FALSE}


c1 <- count(fix_si,missing) %>% arrange(desc(n))

kable(c1,format='markdown')

```

Table 5. Missing Species site index values after BEC substitutions

The major missing species after this substitution is Pw.

## Final Conversion

Run SIndex conversion a second time.

```{r si_convert_step3,eval=TRUE,echo=FALSE,message=FALSE,warning=FALSE}


# run the base conversion a second time
# this will fix the missing Pw
# has to come from Ss
fix_si <- base_si_conversion_pass2(fix_si)

fix_si <- assign_missing(fix_si)
fix_si$src <- 'SIndex Conversion(2)'

si_data <- rbind(si_data,fix_si[fix_si$missing == '',])

##fix_si <- fix_si %>% subset(missing != '')

#fix_si$src <- 'missing'

c1 <- count(fix_si,missing) %>% arrange(desc(n))
kable(c1,format='markdown')

```

Table 6.  After running base SIndex conversions a second time

If missing = BLANK, then we are done.


# summary of Conversion Results

```{r eval=TRUE,echo=FALSE,message=FALSE,warning=FALSE}


c2 <- count(si_data,src)

c2$ord <- case_when(
  c2$src == 'PSPL' ~ 1,
  c2$src == 'Spruce Conversion' ~ 2,
  c2$src == 'SIndex Conversion(1)' ~ 3,
  c2$src == 'BEC Conversion' ~ 4,
  c2$src == 'SIndex Conversion(2)' ~ 5,
  TRUE ~ 99
)

c2 <- c2 %>% arrange(ord)

c2$pct <- case_when(
  c2$src == 'PSPL' ~ c2$n/sum(c2$n) * 100 ,
  c2$src == 'Spruce Conversion' ~ c2$n/sum(c2$n) * 100,
  c2$src == 'SIndex Conversion(1)' ~ c2$n/sum(c2$n) * 100,
  c2$src == 'BEC Conversion' ~ c2$n/sum(c2$n) * 100,
  c2$src == 'SIndex Conversion(2)' ~ c2$n/sum(c2$n) * 100,
  TRUE ~ c2$n/sum(c2$n) * 100
)

c2 <- c2 %>% mutate_if(is.numeric, round, digits=1)
 
kable(c2,format='markdown')

```

Table 7. Final results

Notes:  

| src | description |
|:--|:--|
| PSPL | original data from PSPL that has all requires species site index values |
| Spruce Conversion | Spruce conversions from SX to Sw, Se, Ss |
| SIndex Conversion(1) | SIndex site index conversions |
| BEC Conversion | Site index from BEC mean values |
| SIndex Conversion(2) | SIndex conversions run a second time | 

```{r write,eval=TRUE,echo=FALSE,message=FALSE,warning=FALSE}


# write the data

tbl_name <- paste0('site_index_fid')

dbWriteTable(con,tbl_name,si_data,row.names = FALSE,overwrite=TRUE)

# append the missing

dbWriteTable(con,'site_index_bec',avg_BEC_data,row.names = FALSE,overwrite=FALSE,append=TRUE)


```





```{r echo=FALSE,message=FALSE,warning=FALSE}

z <- dbDisconnect(con)

```



End: `r format(Sys.time(),"%c")`