---
title: "Raster Value DataType Impacts"
author: "D. Waddell"
date: "`r Sys.Date()`"
output: html_document
---

Here is an example of how R handles the storage of large(ish) values in a Tif file.  

In the case of the VRI we are interested in storing the feature_id.  

The max value is: 19,258,969


## Simple Example 

Create a 4x4 raster and fill with values ranging from 17840063 to 17840066.  

These values were chosen as they were seen to be causing problems.

```{r echo=FALSE, message=FALSE, warning=FALSE}

library(kableExtra)

# create small raster
m <- matrix(1:4,nrow=2,ncol=2)
raster_example <- terra::rast(m)

# populate with integer values
raster_example[1] <- 17840063
raster_example[2] <- 17840064
raster_example[3] <- 17840065
raster_example[4] <- 17840066

# check that values are what we expect
v0 <- as.data.frame(terra::values(raster_example))

names(v0) <- 'Original Value'

kable(v0,format="html") %>%
kable_styling(bootstrap_options = c("striped"),full_width=F,font_size=13,position = 'left')

```

## Write to Tif using specified datatype

Create 3 Tifs using the following datatypes:

- INT4S
- FLT4S
- FLT8S


```{r echo=FALSE, message=FALSE, warning=FALSE}
# note on data type 
# INT4U is available but they are best avoided as R does not support 32-bit unsigned integers.

# write as integer INT4S
terra::writeRaster(raster_example, file="test_i.tif", overwrite=TRUE, datatype = 'INT4S')

# write as float FLT4S
terra::writeRaster(raster_example, file="test_f4.tif", overwrite=TRUE, datatype = 'FLT4S')

# write as float FLT8S
terra::writeRaster(raster_example, file="test_f8.tif", overwrite=TRUE, datatype = 'FLT8S')

```

Now look at what was written in the Tifs.

___

## Integer INT4S

Note that we are using INT4S as INT4U is not supported in R.  

Read the Tif and display values:

```{r echo=FALSE, message=FALSE, warning=FALSE}
# read Tif
ri  <- terra::rast("test_i.tif")

# integer values
v1 <- as.data.frame(terra::values(ri))

names(v1) <- 'Value'

kable(v1,format="html") %>%
kable_styling(bootstrap_options = c("striped"),full_width=F,font_size=13,position = 'left')

```

Here the values are exacly as expected.

___


## Single Precision Floating Point: FLT4S

Read the Tif and display the values: 

```{r echo=FALSE, message=FALSE, warning=FALSE}

rf4 <- terra::rast("test_f4.tif")

# float(values) FLT4S
v2 <- as.data.frame(terra::values(rf4))

names(v2) <- 'Value'

kable(v2,format="html") %>%
kable_styling(bootstrap_options = c("striped"),full_width=F,font_size=13,position = 'left')

```


Here the values are being rounded due to floating point representation.  

According to the documentation:  

FLT4S	-3.4e+38	3.4e+38

So, in theory we should be able to store a single precision value without rounding.

___


## Double Precision Floating Point: FLT8S

Read the Tif and display the values: 

```{r echo=FALSE, message=FALSE, warning=FALSE}

rf8 <- terra::rast("test_f8.tif")


# float(values) FLT8S
v3 <- as.data.frame(terra::values(rf8))

names(v3) <- 'Value'

kable(v3,format="html") %>%
kable_styling(bootstrap_options = c("striped"),full_width=F,font_size=13,position = 'left')



```


Here we see that the values are the same as the original integer values.  

___


## Discussion

Computers store decimal values in 3 pieces: 

- the sign (+/-)
- the exponent (biased exponent)
- the fraction (mantissa)

But the number is stored in binary (base 2).  

So in general, we talk about precision: 

```{r echo=FALSE, message=FALSE, warning=FALSE}
prec <- data.frame('Level' = c('Single Precision','Double Precision'), 'Precision' = c('Approximately 7 decimal digits','Approximately 16 decimal digits'))

kable(prec,format="html") %>%
kable_styling(bootstrap_options = c("striped"),full_width=F,font_size=13,position = 'left')


```



So if you look up precision it is often specified as a range.  

The number that we are trying to represent is 17,840,063    

This is represented in scientific notation as:  `r formatC(17840063,format="e")`

So the 3 at the end is going to cause problems for single precision.   This depends on how it tranlates to binary.  You may or may not lose some digits.  

```{r echo=FALSE, message=FALSE, warning=FALSE}
r1 <- data.frame('Decimal' = c(17840063,17840064,17840065,17840066), 
                 'Binary' = c('1000100000011011110111111','1000100000011011111000000','1000100000011011111000001','1000100000011011111000010'))
  
  
kable(r1,format="html") %>%
kable_styling(bootstrap_options = c("striped"),full_width=F,font_size=13,position = 'left')

```  


So 17840063 and 17840065 are loosing precision due to digit rounding and thus are turning into 17840064 and 17840066.  



___

## Oracle Table

The base data (feature_id) comes from an Oracle Spatial table: whse_forest_vegetation.veg_comp_lyr_r1_poly

The data type for this column is: NUMBER(38)

Which is defined as:

- variable length numeric data
- 38 = number of digits in the number
- creates a column intended for integers

So in the LRDW, the feature_id is stored as a Long Integer.  

___


## Recommendations

To avoid having these types of rounding, it is best to use either Long Integer (INT4S) or Double Precision floating (FLT8S).  

These **MUST** be specified on the write to raster call.  

Note that if no datatype is specified on the write, 'FLT4S' is used.  This will cause problems with large numbers.

It would be my recommendation that we use Long Integer.  

___






