---
title: "PSPL Generate Mean values"
author: "dwaddell"
date: '2022-05-20'
output: md_document
---


# PSPL Method 2022


- generate feature id based site index mean values
- generate BEC mean values using feature_id mean site index values
- generate opening id based site index mean values


requires table:  

- pspl_init


Create the following tables:

- pspl_fid_bec (temp)
- pspl_op_bec (temp)

- pspl_fid_site_index_pre_convert  
- pspl_op_site_index_pre_convert  

- pspl_bec_site_index_pre_convert  


Note: no site index conversions have been applied  

Means are derived using SQL to avoid overtaxing limited Memory in R




Start: `r format(Sys.time(),"%c")`

```{r setup, echo=TRUE,message=TRUE,warning=TRUE}

library(RPostgreSQL)



# set up for schema and user
schema <- 'msyt_2022'
opt <- paste0("-c search_path=",schema)
user_name <- 'postgres'
database <- 'msyt'
con <- dbConnect('PostgreSQL',dbname='msyt',user=user_name,options=opt)


```

# create the feature largest BEC table

- pspl_fid_bec

BEC is assigned based on the largest feature_id contribution

```{sql fid_BEC,connection = con}

-- do some intial clean up

drop table if exists pspl_fid_bec;
drop table if exists pspl_op_bec;

drop table if exists pspl_fid_site_index_pre_convert;
drop table if exists pspl_bec_site_index_pre_convert;
drop table if exists pspl_op_site_index_pre_convert;

drop table if exists pspl_fid_site_index;
drop table if exists pspl_bec_site_index;
drop table if exists pspl_op_site_index;


-- create temp table to update bec from pspl_init
-- uses the largest contributor

create table pspl_fid_bec as 
with
	-- count the number of points
	sum_bec as (select count(*) as num_bec,feature_id,bec_zone,bec_subzone 
								from pspl_init 
								group by 2,3,4
								order by 2,3,4 desc),
	-- assign rank 1 to the max
	sum_bec2 as (select num_bec,feature_id,bec_zone,bec_subzone ,
							rank() over (partition by feature_id order by feature_id,num_bec desc) rn
								from sum_bec),
	-- select the first row from each feature_id
	sum_bec3 as (select distinct on (feature_id) feature_id,bec_zone,bec_subzone from sum_bec2 order by feature_id)
select * from sum_bec3
;

select count(*) from pspl_fid_bec;


```


# create the opening largest BEC table

- pspl_op_bec

```{sql op_BEC,connection=con}

-- create the pspl_op_bec table

create table pspl_op_bec as
with
	-- count the number of points
	pspl_op as (select * from pspl_init where opening_id is NOT NULL),
	sum_bec as (select count(*) as num_bec,opening_id,bec_zone,bec_subzone 
								from pspl_op group by 2,3,4
								order by 2,3,4 desc),
	-- assign rank 1 to the max
	sum_bec2 as (select num_bec,opening_id,bec_zone,bec_subzone ,
							rank() over (partition by opening_id order by opening_id,num_bec desc) rn
								from sum_bec),
	-- select the first row from each opening_id
	sum_bec3 as (select distinct on (opening_id) opening_id,bec_zone,bec_subzone from sum_bec2 order by opening_id)
select * from sum_bec3
;

select count (*) from pspl_op_bec;


```



### generate feature_id mean values using SQL

- these are the unconverted data
- generate feature_id based si mean values
- any initial Zero si values have been converted to NULL


Take the original PSPL data by pid and generate the feature_id based mean values.



Processing note:

This process requires tuning on 8GB or less processor

ERROR:  out of memory
DETAIL:  Failed on request of size 848 in memory context "Caller tuples".
CONTEXT:  parallel worker

if required can shut down parallell processing  
set max_parallel_workers_per_gather = 2;  

This process runs fine on a 32GB machine as is.  


Cast final values to Numeric(5,1)

```{sql fid_avg, connection=con,output.var="fid"}


drop table if exists pspl_fid_site_index_pre_convert;
create table pspl_fid_site_index_pre_convert as
select
	feature_id,
	cast(avg(at_si) as numeric(5,1)) as at_si,
	cast(avg(ba_si) as numeric(5,1)) as ba_si,
	cast(avg(bg_si) as numeric(5,1)) as bg_si,
	cast(avg(bl_si) as numeric(5,1)) as bl_si,
	cast(avg(cw_si) as numeric(5,1)) as cw_si,
	cast(avg(dr_si) as numeric(5,1)) as dr_si,
	cast(avg(ep_si) as numeric(5,1)) as ep_si,
	cast(avg(fd_si) as numeric(5,1)) as fd_si,
	cast(avg(hm_si) as numeric(5,1)) as hm_si,
	cast(avg(hw_si) as numeric(5,1)) as hw_si,
	cast(avg(lt_si) as numeric(5,1)) as lt_si,
	cast(avg(lw_si) as numeric(5,1)) as lw_si,
	cast(avg(pa_si) as numeric(5,1)) as pa_si,
	cast(avg(pl_si) as numeric(5,1)) as pl_si,
	cast(avg(pw_si) as numeric(5,1)) as pw_si,
	cast(avg(py_si) as numeric(5,1)) as py_si,
	cast(avg(sb_si) as numeric(5,1)) as sb_si,
	cast(avg(se_si) as numeric(5,1)) as se_si,
	cast(avg(ss_si) as numeric(5,1)) as ss_si,
	cast(avg(sw_si) as numeric(5,1)) as sw_si,
	cast(avg(sx_si) as numeric(5,1)) as sx_si,
	cast(avg(yc_si) as numeric(5,1)) as yc_si
from pspl_init
group by feature_id
order by 1
;

create index idx_pspl_fid_si on pspl_fid_site_index_pre_convert(feature_id);



select count (*) as n from pspl_fid_site_index_pre_convert;

```



### generate BEC mean values


- generate BEC mean values using pspl_init
- use SQL 

Note that this uses the PSPL assigned BEC by point  
NOT the feature_id assigned BEC based on largest number of points



```{sql mean_bec,connection=con,output.var="bec"}


drop table if exists pspl_bec_site_index_pre_convert;
create table pspl_bec_site_index_pre_convert as
select
	bec_zone,bec_subzone,
	cast(avg(at_si) as numeric(5,1)) as at_si,
	cast(avg(ba_si) as numeric(5,1)) as ba_si,
	cast(avg(bg_si) as numeric(5,1)) as bg_si,
	cast(avg(bl_si) as numeric(5,1)) as bl_si,
	cast(avg(cw_si) as numeric(5,1)) as cw_si,
	cast(avg(dr_si) as numeric(5,1)) as dr_si,
	cast(avg(ep_si) as numeric(5,1)) as ep_si,
	cast(avg(fd_si) as numeric(5,1)) as fd_si,
	cast(avg(hm_si) as numeric(5,1)) as hm_si,
	cast(avg(hw_si) as numeric(5,1)) as hw_si,
	cast(avg(lt_si) as numeric(5,1)) as lt_si,
	cast(avg(lw_si) as numeric(5,1)) as lw_si,
	cast(avg(pa_si) as numeric(5,1)) as pa_si,
	cast(avg(pl_si) as numeric(5,1)) as pl_si,
	cast(avg(pw_si) as numeric(5,1)) as pw_si,
	cast(avg(py_si) as numeric(5,1)) as py_si,
	cast(avg(sb_si) as numeric(5,1)) as sb_si,
	cast(avg(se_si) as numeric(5,1)) as se_si,
	cast(avg(ss_si) as numeric(5,1)) as ss_si,
	cast(avg(sw_si) as numeric(5,1)) as sw_si,
	cast(avg(sx_si) as numeric(5,1)) as sx_si,
	cast(avg(yc_si) as numeric(5,1)) as yc_si
from pspl_init
group by bec_zone,bec_subzone
order by 1
;

select count(*) as n from pspl_bec_site_index_pre_convert;



```






### generate opening_id averages

- these are the unconverted data


Take the original PSPL data by pid and generate the opening_id based mean values.



```{sql op_avg,connection=con,output.var="op"}

drop table if exists pspl_op_site_index_pre_convert;
create table pspl_op_site_index_pre_convert as
select
	opening_id,
	cast(avg(at_si) as numeric(5,1)) as at_si,
	cast(avg(ba_si) as numeric(5,1)) as ba_si,
	cast(avg(bg_si) as numeric(5,1)) as bg_si,
	cast(avg(bl_si) as numeric(5,1)) as bl_si,
	cast(avg(cw_si) as numeric(5,1)) as cw_si,
	cast(avg(dr_si) as numeric(5,1)) as dr_si,
	cast(avg(ep_si) as numeric(5,1)) as ep_si,
	cast(avg(fd_si) as numeric(5,1)) as fd_si,
	cast(avg(hm_si) as numeric(5,1)) as hm_si,
	cast(avg(hw_si) as numeric(5,1)) as hw_si,
	cast(avg(lt_si) as numeric(5,1)) as lt_si,
	cast(avg(lw_si) as numeric(5,1)) as lw_si,
	cast(avg(pa_si) as numeric(5,1)) as pa_si,
	cast(avg(pl_si) as numeric(5,1)) as pl_si,
	cast(avg(pw_si) as numeric(5,1)) as pw_si,
	cast(avg(py_si) as numeric(5,1)) as py_si,
	cast(avg(sb_si) as numeric(5,1)) as sb_si,
	cast(avg(se_si) as numeric(5,1)) as se_si,
	cast(avg(ss_si) as numeric(5,1)) as ss_si,
	cast(avg(sw_si) as numeric(5,1)) as sw_si,
	cast(avg(sx_si) as numeric(5,1)) as sx_si,
	cast(avg(yc_si) as numeric(5,1)) as yc_si
from pspl_init where opening_id is not null and opening_id not in (0,-99)
group by opening_id
order by 1
;

```




- original values from PSPL are numeric(n,1)
- after averaging need to make decimals equal



```{sql op_join_bec,connection=con}

drop table if exists t1;
alter table pspl_op_site_index_pre_convert rename to t1;

create table pspl_op_site_index_pre_convert as
select 
 a.opening_id,
 a.at_si,
 a.ba_si,
 a.bg_si,
 a.bl_si,
 a.cw_si,
 a.dr_si,
 a.ep_si,
 a.fd_si,
 a.hm_si,
 a.hw_si,
 a.lt_si,
 a.lw_si,
 a.pa_si,
 a.pl_si,
 a.pw_si,
 a.py_si,
 a.sb_si,
 a.se_si,
 a.ss_si,
 a.sw_si,
 a.sx_si,
 a.yc_si,
 b.bec_zone,
 b.bec_subzone
from t1 a
left join pspl_op_bec b using (opening_id);

select now();

```


```{sql fid_join_bec,connection=con}

drop table if exists t1;
alter table pspl_fid_site_index_pre_convert rename to t1;

create table pspl_fid_site_index_pre_convert as
select 
 a.feature_id,
 a.at_si,
 a.ba_si,
 a.bg_si,
 a.bl_si,
 a.cw_si,
 a.dr_si,
 a.ep_si,
 a.fd_si,
 a.hm_si,
 a.hw_si,
 a.lt_si,
 a.lw_si,
 a.pa_si,
 a.pl_si,
 a.pw_si,
 a.py_si,
 a.sb_si,
 a.se_si,
 a.ss_si,
 a.sw_si,
 a.sx_si,
 a.yc_si,
	b.bec_zone,
	b.bec_subzone
from t1 a
left join pspl_fid_bec b using (feature_id);

drop table t1;


drop table pspl_fid_bec;
drop table pspl_op_bec;



select count(*) as n from pspl_fid_site_index_pre_convert;

```





### Export to CSV

```{r export_data }

# pspl_fid_site_index_pre_convert
# pspl_op_site_index_pre_convert
# pspl_bec_site_index_pre_convert

base <- paste0(substr(getwd(),1,1),':/data/data_projects/AR2022/PSPL/si_data')

f1 <- paste0(base,'/pspl_fid_site_index_pre_convert.csv')
q1 <- paste0("copy msyt_2022.pspl_fid_site_index_pre_convert to \'",f1, "\' csv header;")
dbExecute(con,q1)

f2 <- paste0(base,'/pspl_op_site_index_pre_convert.csv')
q2 <- paste0("copy msyt_2022.pspl_op_site_index_pre_convert to \'",f2, "\' csv header;")
dbExecute(con,q2)

f3 <- paste0(base,'/pspl_bec_site_index_pre_convert.csv')
q3 <- paste0("copy msyt_2022.pspl_bec_site_index_pre_convert to \'",f3, "\' csv header;")
dbExecute(con,q3)


```

```{r disconnect}

dbDisconnect(con)

```



End: `r format(Sys.time(),"%c")`