---
title: "Generate Initial PSPL tables"
author: "dwaddell"
date: '2023_01_19'
output: md_document
---


# PSPL Method 2022

Requires: pspl_intersected 

Creates:

- pspl_site_index_mean_bec
- pspl_site_index_mean_fid


no longer producing:

- pspl_site_index_mean_op

These are the mean values tables (grouped)


## PSPL data pre-processing

- Set all 0 values to NULL 
- Join PSPL to VRI opening_id

Note on BEC.  BEC must be consistent between the point set and VRI.

In this case, BEC 12 has been added to the VRI.  

The BEC is based on the opening largest BEC contribution for


## Treatment of NULL values

There are 22 species site index values for each feature_id.  In general, some of these will not have data and thus be null.  When deriving mean values, it is important to exclude these NULL values from the calculation.  It is also important to check that 0 is not substituted for a NULL.  This can happen inadvertently when using a DUCK Typed language such as R.

Start: `r Sys.time()`


### Initialize PostgreSQL Connection

```{r init}


year <- '2022'

library(RPostgreSQL)

# set up for schema and user
schema <- paste0('msyt_',year)
opt <- paste0("-c search_path=",schema)
user_name <- 'results'
database <- 'msyt'
con <- dbConnect('PostgreSQL',dbname='msyt',user=user_name,options=opt)
#con <- dbConnect('PostgreSQL',dbname='msyt',user=user_name)



db_vac <- function(tb){
  
  com <- shQuote(paste0('vacuum analyze ',tb))
  cmd_arg <- c('-d ' ,database,
                    '-c ' ,com)
  system2('psql', args=cmd_arg,stderr=TRUE)
  
}

pg_dump_table <- function(t_name,folder){
  
  # -O required to negate ownership
  
  f_out <- paste0(folder,t_name,'.sql')

  
  q1 <- paste0("-d ",
               database,
               " -O",
                " -t ",
                t_name,
               " -f ",
               f_out )
  
  system2("pg_dump",args=q1,stderr=TRUE,wait=TRUE)
  print(q1)
  
}


```


### Create inital (temp) table

- read: pspl_intersected
- create: pspl_init_t

This contains the entire Provincial set of PSPL points

```{sql null_type , connection=con}

--drop sequence if exists t1_seq;
--create sequence t1_seq;

drop table if exists pspl_init;
drop table if exists pspl_init_t;

select now() as "start create pspl raw initialze";

-- in each unit(n) objectid is unique
-- after the merge, objectid is no longer unique
-- create id as unique

-- use NULLIF to change 0 si values to NULL
-- required so AVG() ignores the NULL values 

-- this is redundant as the intersection process should have set NULLs properly
--  keep just in case

create table pspl_init_t as 
select 
	--nextval('t1_seq') as id,	-- unique id,
	feature_id,
	NULLIF(at_si,0) as at_si,
	NULLIF(ba_si,0) as ba_si,
	NULLIF(bg_si,0) as bg_si,
	NULLIF(bl_si,0) as bl_si,
	NULLIF(cw_si,0) as cw_si,
	NULLIF(dr_si,0) as dr_si,
	NULLIF(ep_si,0) as ep_si,
	NULLIF(fd_si,0) as fd_si,
	NULLIF(hm_si,0) as hm_si,
	NULLIF(hw_si,0) as hw_si,
	NULLIF(lt_si,0) as lt_si,
	NULLIF(lw_si,0) as lw_si,
	NULLIF(pa_si,0) as pa_si,
	NULLIF(pl_si,0) as pl_si,
	NULLIF(pw_si,0) as pw_si,
	NULLIF(py_si,0) as py_si,
	NULLIF(sb_si,0) as sb_si,
	NULLIF(se_si,0) as se_si,
	NULLIF(ss_si,0) as ss_si,
	NULLIF(sw_si,0) as sw_si,
	NULLIF(sx_si,0) as sx_si,
	NULLIF(yc_si,0) as yc_si
	--trim(substring(bgc_label,1,4)) as bec_zone,
	--trim(substring(bgc_label,5,3)) as bec_subzone
from pspl_intersected ;
--where feature_id is not NULL;

select now() as "end init";


```


Initial Table: `r Sys.time()`  

### Index the intial table

```{sql add_index,connection=con}
 
create index m_idx_sr2 on pspl_init_t(feature_id);


```

Index: `r Sys.time()`  

```{r vacuum_table}

tbl <- paste0(schema,'.pspl_init_t')
db_vac(tbl)



```


Vacuum Analyze: `r Sys.time()`  


## Create pre convert table 

- pspl_init

Note that BEC 12 from VRI is being used.  

The VRI has BEC assigned by largest BEC within opening. 

```{sql join_opening, connection = con}

--drop sequence t1_seq;

-- add opening from veg_comp
drop table if exists pspl_init;
create table pspl_init as
select
	--a.id,
	a.feature_id,
	--b.opening_id,
	a.at_si,
	a.ba_si,
	a.bg_si,
	a.bl_si,
	a.cw_si,
	a.dr_si,
	a.ep_si,
	a.fd_si,
	a.hm_si,
	a.hw_si,
	a.lt_si,
	a.lw_si,
	a.pa_si,
	a.pl_si,
	a.pw_si,
	a.py_si,
	a.sb_si,
	a.se_si,
	a.ss_si,
	a.sw_si,
	a.sx_si,
	a.yc_si,
	b.bec_zone,
	b.bec_subzone
from pspl_init_t a
left join veg_comp b using(feature_id)
;

--drop table pspl_init_t;

create index idx_pspl1 on pspl_init(feature_id);
--create index idx_pspl2 on pspl_init(opening_id);

select now();


```


Pspl Init: `r Sys.time()`  


### generate feature_id mean values using SQL

- these are the unconverted data
- generate feature_id based si mean values
- any initial Zero si values have been converted to NULL


Take the original PSPL data by pid and generate the feature_id based mean values.



Processing note:

This process requires 8GB

ERROR:  out of memory
DETAIL:  Failed on request of size 848 in memory context "Caller tuples".
CONTEXT:  parallel worker

if required can shut down parallel processing  
set max_parallel_workers_per_gather = 2;  

This process runs fine on a 32GB machine as is.  


Cast final values to Numeric(5,1)

```{sql fid_avg, connection=con,output.var="fid"}


drop table if exists pspl_site_index_mean_fid;
create table pspl_site_index_mean_fid as
select
	feature_id,
	cast(avg(at_si) as numeric(5,1)) as at_si,
	cast(avg(ba_si) as numeric(5,1)) as ba_si,
	cast(avg(bg_si) as numeric(5,1)) as bg_si,
	cast(avg(bl_si) as numeric(5,1)) as bl_si,
	cast(avg(cw_si) as numeric(5,1)) as cw_si,
	cast(avg(dr_si) as numeric(5,1)) as dr_si,
	cast(avg(ep_si) as numeric(5,1)) as ep_si,
	cast(avg(fd_si) as numeric(5,1)) as fd_si,
	cast(avg(hm_si) as numeric(5,1)) as hm_si,
	cast(avg(hw_si) as numeric(5,1)) as hw_si,
	cast(avg(lt_si) as numeric(5,1)) as lt_si,
	cast(avg(lw_si) as numeric(5,1)) as lw_si,
	cast(avg(pa_si) as numeric(5,1)) as pa_si,
	cast(avg(pl_si) as numeric(5,1)) as pl_si,
	cast(avg(pw_si) as numeric(5,1)) as pw_si,
	cast(avg(py_si) as numeric(5,1)) as py_si,
	cast(avg(sb_si) as numeric(5,1)) as sb_si,
	cast(avg(se_si) as numeric(5,1)) as se_si,
	cast(avg(ss_si) as numeric(5,1)) as ss_si,
	cast(avg(sw_si) as numeric(5,1)) as sw_si,
	cast(avg(sx_si) as numeric(5,1)) as sx_si,
	cast(avg(yc_si) as numeric(5,1)) as yc_si
from pspl_init
group by feature_id
order by 1
;

create index idx_pspl_fid_si on pspl_site_index_mean_fid(feature_id);



select count (*) as n from pspl_site_index_mean_fid;

```


Mean si FID: `r Sys.time()`  

### generate BEC mean values


- generate BEC mean values using pspl_init


Note that this uses the BEC 12 assigned BEC updated in  VRI   




```{sql mean_bec,connection=con,output.var="bec"}


drop table if exists pspl_site_index_mean_bec;
create table pspl_site_index_mean_bec as
select
	bec_zone,bec_subzone,
	cast(avg(at_si) as numeric(5,1)) as at_si,
	cast(avg(ba_si) as numeric(5,1)) as ba_si,
	cast(avg(bg_si) as numeric(5,1)) as bg_si,
	cast(avg(bl_si) as numeric(5,1)) as bl_si,
	cast(avg(cw_si) as numeric(5,1)) as cw_si,
	cast(avg(dr_si) as numeric(5,1)) as dr_si,
	cast(avg(ep_si) as numeric(5,1)) as ep_si,
	cast(avg(fd_si) as numeric(5,1)) as fd_si,
	cast(avg(hm_si) as numeric(5,1)) as hm_si,
	cast(avg(hw_si) as numeric(5,1)) as hw_si,
	cast(avg(lt_si) as numeric(5,1)) as lt_si,
	cast(avg(lw_si) as numeric(5,1)) as lw_si,
	cast(avg(pa_si) as numeric(5,1)) as pa_si,
	cast(avg(pl_si) as numeric(5,1)) as pl_si,
	cast(avg(pw_si) as numeric(5,1)) as pw_si,
	cast(avg(py_si) as numeric(5,1)) as py_si,
	cast(avg(sb_si) as numeric(5,1)) as sb_si,
	cast(avg(se_si) as numeric(5,1)) as se_si,
	cast(avg(ss_si) as numeric(5,1)) as ss_si,
	cast(avg(sw_si) as numeric(5,1)) as sw_si,
	cast(avg(sx_si) as numeric(5,1)) as sx_si,
	cast(avg(yc_si) as numeric(5,1)) as yc_si
from pspl_init
group by bec_zone,bec_subzone
order by 1
;

select count(*) as n from pspl_site_index_mean_bec;



```


BEC Mean si: `r Sys.time()`  

- original values from PSPL are numeric(n,1)
- values in PostreSQL are double



```{r export_data , eval=FALSE}

dbDisconnect(con)


```



End: `r Sys.time()`