---
title: "Standard Approach to Rasterizing VRI"
author: "D. Waddell"
date: "`r Sys.Date()`"
output: md_document
---


Develop a standardized approach to rasterization for FAIB data processing.   

AR2022


Using only R-4.1.3 
Package: sf  

No GDAL or Python installed.  

Workstation config: 32GB RAM  


Rasterize VRI from PostgreSQL 
Previously impossible on 32 GB machine using R.  

sf::gdal_utils relies on backed C++ gdal rasterize function.  
This relieves the memory load from R.  

Links to: GEOS 3.9.1, GDAL 3.2.1, PROJ 7.2.1  




Start: `r Sys.time()`

## Raster Standards


### Spatial Extent

| Extent | Value |
|:-------|:------|
| xmin | 273287.5 |
| xmax | 1870587.5 |
| ymin | 367787.5 |
| ymax | 1735787.5 |

### No Data Value

Value = 0

### Output Data Type

Int32

In the GDAL documentation, the list of supported integer data types includes:

- Int16 (short)
- Int32 (long)

Since the max value for Int32 is 2,147,483,647 this should be adequate to allow for future feature_ids.




## Method: PostgreSQL to TIF using sf::gdal_utils

Links to a local PostgreSQL database that used an Oracle Foreign data wrapper to create a copy of idwprod1.veg_comp_lyr_r1_poly.  PostgreSQL table is called veg_comp_spatial and only contains feature_id and wkb_geometry. 


Define standard extent , noData Value and output dataType

```{r standard_values}


# standardize extents
xmin <- 273287.5
xmax <- 1870587.5
ymin <- 367787.5
ymax <- 1735787.5

nodata <- 0

dataType <- 'Int32'

```


Read PostgreSQL spatial table and export to Tif  

Set the Tif layer name to be feature_id

```{r create_tif_from_postgresql}



src <- "PG:dbname='msyt' user='postgres'"
spatial_table <- 'msyt_2022.veg_comp_spatial'
dest <- paste0(substr(getwd(),1,1),':/data/data_projects/AR2022/PSPL/vri_raster.tif')


sf::gdal_utils("rasterize",src,dest,options = 
             c('-tr','100',' 100',
                '-te',xmin,ymin,xmax,ymax,
                '-ot', dataType,
                '-l', spatial_table,
                '-a', 'FEATURE_ID' ,
                '-a_srs','EPSG:3005',
                '-a_nodata', nodata,
                '-co','COMPRESS=LZW'),
                '-overwrite')


# update for NA
r1 <- terra::rast(dest)
r1[is.na(r1)]  <- 0

# name the layer: feature_id
names(r1) <- 'feature_id'

# overwrite to destination
terra::writeRaster(r1, dest, datatype='INT4U', overwrite=TRUE)




```


Cross check the feature id 

```{r cross_check}

library(tidyverse)
library(data.table)

con <- RPostgreSQL::dbConnect('PostgreSQL',dbname='msyt')

psql_fid <- DBI::dbGetQuery(con,'select feature_id from msyt_2022.veg_comp')

RPostgreSQL::dbDisconnect(con)

# read the Tif that was written
dest <- paste0(substr(getwd(),1,1),':/data/data_projects/AR2022/PSPL/vri_raster.tif')
r1 <- terra::rast(dest)

tif_fid <- as.data.table(terra::values(r1))

tif_fid <- unique(tif_fid)
names(tif_fid) <- 'feature_id'

# tif values should only come from the VRI
# if there are values in the TIF that aren't in the VRI spatial
# there is a problem (like an integer value rounding as an example)
tif_only <- tif_fid %>% subset(!feature_id %in% psql_fid$feature_id)

# there will be raster values missing from TIF
# this is an artifact of the rasertization process
# and is expected
psql_only <- psql_fid %>% subset(!feature_id %in% tif_fid$feature_id)





```



## Tif Values NOT found in VRI spatial

tif values should only come from the VRI  
if there are values in the TIF that aren't in the VRI spatial  
there is a problem (like an integer value rounding as an example)  

Only in Tif: `r nrow(tif_only)` rows

```{r check_values}

if (nrow(tif_only ==1)){
  kableExtra::kable(tif_only)
}

```


## VRI spatial features NOT found in Raster

there will be raster values missing from TIF  
this is an artifact of the rasertization process  
and is expected

In Postgresql, **NOT** in Tif `r nrow(psql_only)`  


PostgreSQL -> Tif: `r Sys.time()`




End: `r Sys.time()`


